### 2020-03-24 eca2019proceedings.tex
Import

\documentclass[a4paper,oneside]{book}
\usepackage[utf8x,utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{fancyhdr}
\usepackage{paralist}
\usepackage{tocloft}
\usepackage{imakeidx}
\usepackage[hidelinks]{hyperref}
\usepackage[open,openlevel=1]{bookmark}

\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}}

%\usepackage[colorlinks]{hyperref}

\makeindex[name=authors,title=Index of Authors]

\makeatletter
\let\origps@plain\ps@plain
\newcommand\MakePlainPagestyleEmpty{\let\ps@plain\ps@empty}
\newcommand\MakePlainPagestylePlain{\let\ps@plain\origps@plain}
\makeatother

\pagestyle{fancy}
\fancyhf{}% Clear page header/footer
\renewcommand{\headrulewidth}{0pt}% No header rule
\fancyfoot[C]{\thepage}

\newcommand{\insertmydocument}[4]%
           { % Syntax: \insertmydocument{Toc level}{Title}{Subtitle}{File}
             % Requires: tocloft hyperref pdfpages
             \newpage
             \phantomsection
             \cftaddtitleline{toc}{#1}{#2}{\thepage}
             \cftchapterprecistoc{#3}
            \includepdf[pages=-,pagecommand={\pagestyle{fancy}}]{#4}
           }

\makeindex

\begin{document}

\frontmatter
\includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/cover}
\setcounter{page}{1}
\includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/firstpages}

\section*{Committees}
	\addcontentsline{toc}{chapter}{Committees}
	\subsection*{General chairs}
	\begin{compactitem}[]
	\item[] Bart Verheij
	\item[] Marco Wiering
	\end{compactitem}

	\subsection*{Contact \& administration}
	\begin{compactitem}[]
	\item[] Elina Sietsema
	\item[] Carlijne de Vries
	\item[] Sarah van Wouwe
	\end{compactitem}

	\subsection*{Local organisation}
	\begin{compactitem}[]
		\item[] Luca Bandelli
		\item[] Abe Brandsma
		\item[] Tomasz Darmetko
		\item[] Mingcheng Ding
		\item[] Ana Dugeniuc
		\item[] Joel During
		\item[] Ameer Islam
		\item[] Siebert Looije
		\item[] Ren\'e Mellema
		\item[] Michaela Mr\`azkov\'a
		\item[] Annet Onnes
		\item[] Benjamin Shafrey
		\item[] Sjaak ten Caat
		\item[] Albert Thie
		\item[] Jelmer van der Linde
		\item[] Luuk van Keeken
		\item[] Paul Veldhuyzen
		\item[] Randy Wind
		\item[] Galiya Yeshmagambetova
	\end{compactitem}

	\subsection*{Program committee}
	\begin{compactitem}[]
		\item[] Stylianos Asteriadis, Maastricht University
		\item[] Reyhan Aydogan, Delft University of Technology
		\item[] Floris Bex, Utrecht University
		\item[] Michael Biehl, University of Groningen
		\item[] Mauro Birattari, Universit\'e Libre de Bruxelles
		\item[] Hendrik Blockeel, Katholieke Universiteit Leuven
		\item[] Hans L. Bodlaender, Utrecht University
		\item[] Sander Bohte, Centrum Wiskunde \& Informatica (CWI)
		\item[] Peter Bosman, Centrum Wiskunde \& Informatica (CWI)
		\item[] Tibor Bosse, Vrije Universiteit Amsterdam
		\item[] Bruno Bouzy, Paris Descartes University
		\item[] Frances Brazier, Delft University of Technology
		\item[] Bert Bredeweg, University of Amsterdam
		\item[] Tristan Cazenave, Universit\'e Paris Dauphine
		\item[] Tom Claassen, Radboud University Nijmegen
		\item[] Walter Daelemans, University of Antwerp
		\item[] Gregoire Danoy, University of Luxembourg
		\item[] Mehdi Dastani, Utrecht University
		\item[] Patrick De Causmaecker, Katholieke Universiteit Leuven
		\item[] Martine De Cock, University of Washington Tacoma
		\item[] Mathijs De Weerdt, Delft University of Technology
		\item[] Beno\^it Depaire, Hasselt University
		\item[] Frank Dignum, Utrecht University
		\item[] Virginia Dignum, Delft University of Technology
		\item[] Kurt Driessens, Maastricht University
		\item[] Madalina Drugan, Technical University of Eindhoven
		\item[] Sjur Dyrkolbotn, Western Norway University of Applied Sciences
		\item[] Jason Farquhar, Radboud University Nijmegen
		\item[] Ad Feelders, Utrecht University
		\item[] Bart Goethals, University of Antwerp
		\item[] Pascal Gribomont, University of Liège
		\item[] Perry Groot, Radboud University Nijmegen
		\item[] Marc Gyssens, Universiteit Hasselt
		\item[] Frank Harmsen, Ernst \& Young Advisory
		\item[] Maaike Harbers, Rotterdam University of Applied Sciences
		\item[] Tom Heskes, Radboud University Nijmegen
		\item[] Koen Hindriks, Delft University of Technology
		\item[] Arjen Hommersom, Open University of the Netherlands
		\item[] Mark Hoogendoorn, Vrije Universiteit Amsterdam
		\item[] Gerda Janssens, Katholieke Universiteit Leuven
		\item[] Maurits Kaptein, Eindhoven University of Technology
		\item[] Uzay Kaymak, Eindhoven University of Technology
		\item[] Walter Kosters, Leiden University
		\item[] Johan Kwisthout, Radboud University Nijmegen
		\item[] Tom Lenaerts, Université Libre de Bruxelles
		\item[] Marco Loog, Delft University of Technology
		\item[] Peter Lucas, Radboud University
		\item[] Elena Marchiori, Radboud University Nijmegen
		\item[] Wannes Meert, Katholieke Universiteit Leuven
		\item[] John-Jules Meyer, Utrecht University
		\item[] Peter Nov\'ak, Delft University of Technology
		\item[] Ann Now\'e, Vrije Universiteit Brussel
		\item[] Aske Plaat, Leiden University
		\item[] Eric Postma, Tilburg University
		\item[] Henry Prakken, University of Utrecht, University of Groningen
		\item[] Jan Ramon, INRIA
		\item[] Silja Renooij, Utrecht University
		\item[] Nico Roos, Maastricht University
		\item[] Stefan Schlobach, Vrije Universiteit Amsterdam
		\item[] Pierre-Yves Schobbens, University of Namur
		\item[] Johannes Scholtes, Maastricht University
		\item[] Lambert Schomaker, University of Groningen
		\item[] Martijn Schut, Universiteit van Amsterdam
		\item[] Evgueni Smirnov, Maastricht University
		\item[] Matthijs T. J. Spaan, Delft University of Technology
		\item[] Gerasimos Spanakis, Maastricht University
		\item[] Jennifer Spenader, University of Groningen
		\item[] Ida Sprinkhuizen-Kuyper, Radboud University Nijmegen
		\item[] Thomas Stützle, Universit\'e Libre de Bruxelles
		\item[] Johan Suykens, Katholieke Universiteit Leuven
		\item[] Niels Taatgen, University of Groningen
		\item[] Annette Ten Teije, Vrije Universiteit Amsterdam
		\item[] Dirk Thierens, Utrecht University
		\item[] Karl Tuyls, University of Liverpool
		\item[] Antal van den Bosch, Radboud University Nijmegen
		\item[] Egon L. van den Broek, Utrecht University
		\item[] Jaap van den Herik, Leiden University
		\item[] Linda van der Gaag, Utrecht University
		\item[] Peter van der Putten, Leiden University, Pegasystems
		\item[] Leon van der Torre, University of Luxembourg
		\item[] Natalie van der Wal, Vrije Universiteit Amsterdam
		\item[] Tim van Erven, Leiden University
		\item[] Marcel van Gerven, Radboud University Nijmegen
		\item[] Frank van Harmelen, Vrije Universiteit Amsterdam
		\item[] Martijn van Otterlo, Vrije Universiteit Amsterdam
		\item[] M. Birna van Riemsdijk, Delft University of Technology
		\item[] Maarten van Someren, University of Amsterdam
		\item[] Marieke van Vugt, University of Groningen
		\item[] Menno van Zaanen, Tilburg University
		\item[] Joaquin Vanschoren, Eindhoven University of Technology
		\item[] Marina Velikova, Radboud University Nijmegen
		\item[] Remco Veltkamp, Utrecht University
		\item[] Joost Vennekens, Katholieke Universiteit Leuven
		\item[] Katja Verbeeck, Technologiecampus Gent
		\item[] Rineke Verbrugge, University of Groningen
		\item[] Michel Verleysen, Universit\'e Catholique de Louvain
		\item[] Sicco Verwer, Delft University of Technology
		\item[] Arnoud Visser, Universiteit van Amsterdam
		\item[] Willem Waegeman, Ghent University
		\item[] Martijn Warnier, Delft University of Technology
		\item[] Gerhard Weiss, Maastricht University
		\item[] Floris Wiesman, Academic Medical Center Amsterdam
		\item[] Jef Wijsen, University of Mons
		\item[] Mark H. M. Winands, Maastricht University
		\item[] Radboud Winkels, Universiteit van Amsterdam
		\item[] Cees Witteveen, Delft University of Technology
		\item[] Marcel Worring, University of Amsterdam
		\item[] Yingqian Zhang, Eindhoven University of Technology
	\end{compactitem}

\include{preface}

\newpage
\pdfbookmark[chapter]{Table of Contents}{toc}
\tableofcontents

\mainmatter
\MakePlainPagestyleEmpty

\include{papers-with-names}

\printindex[authors]

\includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/back}

\end{document}

### 2020-03-24 papers-with-names.tex
Import

\part{Long papers}

\index[authors]{Aakhus, Mark}
\pdfbookmark[chapter]{Argumentative Design and Polylogue}{paper-long-10}
\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/10longGascón.doc.pdf}

\index[authors]{Bermejo-Luque, Lilian}
\pdfbookmark[chapter]{What is wrong with deductivism?}{paper-long-11}
\insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/11LongGoddu.doc.pdf}

\index[authors]{Blair, J. Anthony}
\pdfbookmark[chapter]{Is there an informal logic approach to argument?}{paper-long-12}
\insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/12longHannkenilljes.docx.pdf}

\index[authors]{Bodlović, Petar}
\pdfbookmark[chapter]{Structural differences between practical and cognitive presumptions}{paper-long-13}
\insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlović}{pdfs/long/13longHenning.docx.pdf}

\index[authors]{Cacean, Sebastian}
\pdfbookmark[chapter]{Reliability of Argument Mapping}{paper-long-14}
\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/14longHoffmann.doc.pdf}

\index[authors]{Castro, Diego}
\pdfbookmark[chapter]{Critical discussion for sub-optimal settings}{paper-long-15}
\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/15longHoppmann.doc.pdf}

\index[authors]{Corredor, Cristina}
\pdfbookmark[chapter]{Democratic Legitimacy and Acts of Dissent}{paper-long-16}
\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/16longJackson.doc.pdf}

\index[authors]{Freeman, James}
\pdfbookmark[chapter]{Strength of reasons for moral dissent}{paper-long-18}
\insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/18longLewinski.doc.pdf}

\index[authors]{Gascón, José Ángel}
\pdfbookmark[chapter]{Where are dissent and reasons in epistemic justification?}{paper-long-19}
\insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{José Ángel Gascón}{pdfs/long/19longLicato.doc.pdf}

\index[authors]{Goddu, G.C.}
\pdfbookmark[chapter]{Justifying Questions?}{paper-long-1}
\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/1longAakhus.docx.pdf}

\index[authors]{Hannken-Illjes, Kati}
\pdfbookmark[chapter]{Ethnography of Argumentation}{paper-long-20}
\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/20longLumer.doc.pdf}

\index[authors]{Henning, Tempest M}
\pdfbookmark[chapter]{“’I said what I said’ - Black women and argumentative politeness norms”}{paper-long-21}
\insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/21longMosaka.doc.pdf}

\index[authors]{Hoffmann, Michael H.G.}
\pdfbookmark[chapter]{The Argument Assessment Tutor (AAT)}{paper-long-22}
\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/22longReijven.doc.pdf}

\index[authors]{Hoppmann, Michael J.}
\pdfbookmark[chapter]{Grice, Machine Head and the problem of overexpressed premises}{paper-long-23}
\insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/23longSadek.doc.pdf}

\index[authors]{Zhang, Sally Jackson, Scott Jacobs, Xiaoqi}
\pdfbookmark[chapter]{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{paper-long-24}
\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/24longSinclair.doc.pdf}

\index[authors]{Lewiński, Marcin}
\pdfbookmark[chapter]{Speech act pluralism in argumentative polylogues}{paper-long-25}
\insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewiński}{pdfs/long/25longTindale.docx.pdf}

\index[authors]{Cooper, John Licato, Michael}
\pdfbookmark[chapter]{Evaluating relevance in analogical arguments through warrant-based reasoning}{paper-long-27}
\insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/27longZemplen.doc.pdf}

\index[authors]{Lumer, Christoph}
\pdfbookmark[chapter]{Arguments from expert opinion – An epistemological approach}{paper-long-3}
\insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/3LongBermejo-Luque.doc.pdf}

\index[authors]{Mosaka, Tshepo Bogosi}
\pdfbookmark[chapter]{All-out attack}{paper-long-4}
\insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/4longBlair.docx.pdf}

\index[authors]{Reijven, Menno H.}
\pdfbookmark[chapter]{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{paper-long-5}
\insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H. Reijven}{pdfs/long/5longBodlović.doc.pdf}

\index[authors]{Sadek, Karim}
\pdfbookmark[chapter]{Disagreement, public reasoning, and (non-)authoritarian argumentation}{paper-long-6}
\insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/6longCacean.docx.pdf}

\index[authors]{Sinclair, Sean}
\pdfbookmark[chapter]{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{paper-long-7}
\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/7longCastro.doc.pdf}

\index[authors]{Tindale, Christopher W.}
\pdfbookmark[chapter]{Strange Fish: Belief and the roots of disagreement}{paper-long-8}
\insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/8longCorredor.docx.pdf}

\index[authors]{Zemplen, Gabor}
\pdfbookmark[chapter]{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{paper-long-9}
\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Gabor Zemplen}{pdfs/long/9longFreeman.doc.pdf}

% \addtocontents{toc}{\protect\newpage}
\part{Regular papers}

\part{Thematic papers}

### 2020-03-24 papers.tex
Import

--- 2020-03-24 papers-with-names.tex
@@
 
-\index[authors]{Aakhus, Mark}
-\pdfbookmark[chapter]{Argumentative Design and Polylogue}{paper-long-10}
 \insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/10longGascón.doc.pdf}
-
-\index[authors]{Bermejo-Luque, Lilian}
-\pdfbookmark[chapter]{What is wrong with deductivism?}{paper-long-11}
 \insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/11LongGoddu.doc.pdf}
-
-\index[authors]{Blair, J. Anthony}
-\pdfbookmark[chapter]{Is there an informal logic approach to argument?}{paper-long-12}
 \insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/12longHannkenilljes.docx.pdf}
-
-\index[authors]{Bodlović, Petar}
-\pdfbookmark[chapter]{Structural differences between practical and cognitive presumptions}{paper-long-13}
 \insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlović}{pdfs/long/13longHenning.docx.pdf}
-
-\index[authors]{Cacean, Sebastian}
-\pdfbookmark[chapter]{Reliability of Argument Mapping}{paper-long-14}
 \insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/14longHoffmann.doc.pdf}
-
-\index[authors]{Castro, Diego}
-\pdfbookmark[chapter]{Critical discussion for sub-optimal settings}{paper-long-15}
 \insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/15longHoppmann.doc.pdf}
-
-\index[authors]{Corredor, Cristina}
-\pdfbookmark[chapter]{Democratic Legitimacy and Acts of Dissent}{paper-long-16}
 \insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/16longJackson.doc.pdf}
-
-\index[authors]{Freeman, James}
-\pdfbookmark[chapter]{Strength of reasons for moral dissent}{paper-long-18}
 \insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/18longLewinski.doc.pdf}
-
-\index[authors]{Gascón, José Ángel}
-\pdfbookmark[chapter]{Where are dissent and reasons in epistemic justification?}{paper-long-19}
 \insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{José Ángel Gascón}{pdfs/long/19longLicato.doc.pdf}
-
-\index[authors]{Goddu, G.C.}
-\pdfbookmark[chapter]{Justifying Questions?}{paper-long-1}
 \insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/1longAakhus.docx.pdf}
-
-\index[authors]{Hannken-Illjes, Kati}
-\pdfbookmark[chapter]{Ethnography of Argumentation}{paper-long-20}
 \insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/20longLumer.doc.pdf}
-
-\index[authors]{Henning, Tempest M}
-\pdfbookmark[chapter]{“’I said what I said’ - Black women and argumentative politeness norms”}{paper-long-21}
 \insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/21longMosaka.doc.pdf}
-
-\index[authors]{Hoffmann, Michael H.G.}
-\pdfbookmark[chapter]{The Argument Assessment Tutor (AAT)}{paper-long-22}
 \insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/22longReijven.doc.pdf}
-
-\index[authors]{Hoppmann, Michael J.}
-\pdfbookmark[chapter]{Grice, Machine Head and the problem of overexpressed premises}{paper-long-23}
 \insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/23longSadek.doc.pdf}
-
-\index[authors]{Zhang, Sally Jackson, Scott Jacobs, Xiaoqi}
-\pdfbookmark[chapter]{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{paper-long-24}
 \insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/24longSinclair.doc.pdf}
-
-\index[authors]{Lewiński, Marcin}
-\pdfbookmark[chapter]{Speech act pluralism in argumentative polylogues}{paper-long-25}
 \insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewiński}{pdfs/long/25longTindale.docx.pdf}
-
-\index[authors]{Cooper, John Licato, Michael}
-\pdfbookmark[chapter]{Evaluating relevance in analogical arguments through warrant-based reasoning}{paper-long-27}
 \insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/27longZemplen.doc.pdf}
-
-\index[authors]{Lumer, Christoph}
-\pdfbookmark[chapter]{Arguments from expert opinion – An epistemological approach}{paper-long-3}
 \insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/3LongBermejo-Luque.doc.pdf}
-
-\index[authors]{Mosaka, Tshepo Bogosi}
-\pdfbookmark[chapter]{All-out attack}{paper-long-4}
 \insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/4longBlair.docx.pdf}
-
-\index[authors]{Reijven, Menno H.}
-\pdfbookmark[chapter]{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{paper-long-5}
 \insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H.
 Reijven}{pdfs/long/5longBodlović.doc.pdf}
-
-\index[authors]{Sadek, Karim}
-\pdfbookmark[chapter]{Disagreement, public reasoning, and (non-)authoritarian argumentation}{paper-long-6}
 \insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/6longCacean.docx.pdf}
-
-\index[authors]{Sinclair, Sean}
-\pdfbookmark[chapter]{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{paper-long-7}
 \insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/7longCastro.doc.pdf}
-
-\index[authors]{Tindale, Christopher W.}
-\pdfbookmark[chapter]{Strange Fish: Belief and the roots of disagreement}{paper-long-8}
 \insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/8longCorredor.docx.pdf}
-
-\index[authors]{Zemplen, Gabor}
-\pdfbookmark[chapter]{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{paper-long-9}
 \insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Gabor Zemplen}{pdfs/long/9longFreeman.doc.pdf}

### 2020-03-24 preface.tex
Import

\section*{Preface}
\addcontentsline{toc}{chapter}{Preface}

BNAIC is the annual Benelux Conference on Artificial Intelligence. In 2017, the 29\textsuperscript{th} edition of BNAIC is organized by the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), University of Groningen, under the auspices of the Benelux Association for Artificial Intelligence (BNVKI) and the Dutch Research School for Information and Knowledge Systems (SIKS).

BNAIC 2017 takes place in Het Kasteel, Melkweg 1, Groningen, The Netherlands, on Wednesday November 8 and Thursday November 9, 2017. BNAIC 2017 includes invited speakers, research presentations, posters, demonstrations, a deep learning workshop (organized by our sponsor NVIDIA) and a research and business session.

The four BNAIC 2017 keynote speakers are:

\begin{itemize}
	\item 
Marco Dorigo, Universit\'{e} Libre de Bruxelles\\
\emph{Swarm Robotics: Current Research Directions at IRIDIA}

	\item 
Laurens van der Maaten, Facebook AI Research\\
\emph{From Visual Recognition to Visual Understanding}

	\item 
Luc Steels, Institute for Advanced Studies (ICREA), Barcelona\\
\emph{Digital Replicants and Mind-Uploading
}

	\item 
Rineke Verbrugge, University of Groningen\\
\emph{Recursive Theory of Mind: Between Logic and Cognition}
\end{itemize}

\noindent Three FACt talks (FACulty focusing on the FACts of Artificial Intelligence) are scheduled:

\begin{itemize}
	\item 
Bert Bredeweg, Universiteit van Amsterdam\\
\emph{Humanly AI: Creating smart people with AI}
	\item Eric Postma, Tilburg University\\
\emph{Towards Artificial Human-like Intelligence}
	\item Geraint Wiggins, Queen Mary University of London/Vrije Universiteit Brussel\\
\emph{Introducing Computational Creativity}
\end{itemize}

\noindent Authors were invited to submit papers on all aspects of Artificial Intelligence. This year we have received 68 submissions in total. Of the 30 submitted Type A regular papers, 11 (37\%) were accepted for oral presentation, and 14 (47\%) for poster presentation. 5 (17\%) were rejected. Of the 19 submitted Type B compressed contributions, 17 (89\%) were accepted for oral presentation, and 2 (11\%) for poster presentation. None were rejected. All 6 submitted Type C demonstration abstracts were accepted. Of the submitted 13 Type D thesis abstracts, 5 (38\%) were accepted for oral presentation, and 8 (62\%) for poster presentation. None were rejected. The selection was made using peer review. Each submission was assigned to three members of the program committee, and their expert reviews were the basis for our decisions.

All submissions accepted for oral or poster presentations and all demonstration abstracts appear in the electronic preproceedings, made available on the conference web site during the conference (\url{http://bnaic2017.ai.rug.nl/}). All 11 Type A regular papers accepted for oral presentation will appear in the postproceedings, to be published in the Springer CCIS series after the conference.

The BNAIC 2017 conference would not be possible without the support and efforts of many. We thank the members of the program committee for their constructive and scholarly reviews. We are grateful to 
    Elina Sietsema, Carlijne de Vries and 
		Sarah van Wouwe, members of the administrative staff at the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), for their tireless and reliable support. We thank our local organisation team 
		Luca Bandelli,
    Abe Brandsma,
    Tomasz Darmetko,
    Mingcheng Ding,
    Ana Dugeniuc,
    Joel During,
    Ameer Islam,
    Siebert Looije,
    Ren\'{e} Mellema,
    Michaela Mr\'{a}zkov\'{a},
    Annet Onnes,
    Benjamin Shaffrey,
    Sjaak ten Caat,
    Albert Thie,
    Jelmer van der Linde,
    Luuk van Keeken,
    Paul Veldhuyzen,
    Randy Wind, and
    Galiya Yeshmagambetova, 
all students in our BSc and MSc Artificial Intelligence programs, for enthusiastically volunteering to help out in many ways. We thank Annet Onnes for preparing the preproceedings, Jelmer van der Linde for developing the web site, Randy Wind for designing the program leaflet, and Albert Thie for coordinating the local organisation.

We are grateful to our sponsors for their generous support of the conference:
\begin{itemize}
%		
	\item 
Target Holding
	\item 
NVIDIA Deep Learning Institute
%
	\item 
Anchormen
	\item 
Quint
	\item 
the Netherlands Research School for Information and Knowledge Systems (SIKS)
	\item 
SIM-CI
%
	\item 
Textkernel
	\item 
LuxAI
	\item 
IOS Press
	\item 
Stichting Knowledge-Based Systems (SKBS)
	\item 
SSN Adaptive Intelligence 
\end{itemize}

\noindent 
We wish you a pleasant conference!

\begin{flushright}
Bart Verheij \& Marco Wiering
\end{flushright}

### 2020-03-24 authors.py

@@ -1,0 +1,44 @@
+#!/usr/bin/env python
+from __future__ import print_function
+import re
+import sys
+
+pattern = re.compile(r'^\\insertmydocument\{chapter\}\{(?P<title>.+?)\}\{(?P<authors>.+?)\}\{(?P<file>.+?)\}$')
+
+def parse_authors(authors):
+	try:
+		rest, last = authors.rsplit(' and ', 1)
+		rest = rest.split(', ')
+		return [parse_author(author) for author in (rest + [last])]
+	except ValueError:
+		return [parse_author(authors)]
+
+
+def parse_author(author):
+	try:
+		first_name, last_name = author.rsplit(' ', 1)
+		return (last_name, first_name)
+	except ValueError as e:
+		raise Exception('Stupid name: "{}"'.format(author))
+
+
+def parse_filename(filename):
+	match = re.match(r'pdfs/(?P<type>\w+)/(?P<id>\d+)', filename)
+	return match.group('type') + '-' + match.group('id')
+
+
+if __name__ == '__main__':
+	for line in sys.stdin:
+		line = line.rstrip()
+		match = pattern.match(line)
+		if match:
+			for author in parse_authors(match.group('authors')):
+				print('\index[authors]{{{0}, {1}}}'.format(*author))
+			print('\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
+				section=match.group('title'),
+				id=parse_filename(match.group('file'))))
+		print(line)
+		if match:
+			print("")
+		
+	print("Done! Don't forget to enable imakeidx:\n  \usepackage{imakeidx}\n  \makeindex[name=authors,title=Index of Authors,options=-r]", file=sys.stderr)

### 2020-03-24 papers.tex
Get long papers to compile

@@
 
-\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/10longGascón.doc.pdf}
-\insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/11LongGoddu.doc.pdf}
-\insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/12longHannkenilljes.docx.pdf}
-\insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlović}{pdfs/long/13longHenning.docx.pdf}
-\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/14longHoffmann.doc.pdf}
-\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/15longHoppmann.doc.pdf}
-\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/16longJackson.doc.pdf}
-\insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/18longLewinski.doc.pdf}
-\insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{José Ángel Gascón}{pdfs/long/19longLicato.doc.pdf}
-\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/1longAakhus.docx.pdf}
-\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/20longLumer.doc.pdf}
-\insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/21longMosaka.doc.pdf}
-\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/22longReijven.doc.pdf}
-\insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/23longSadek.doc.pdf}
-\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/24longSinclair.doc.pdf}
-\insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewiński}{pdfs/long/25longTindale.docx.pdf}
-\insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/27longZemplen.doc.pdf}
-\insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/3LongBermejo-Luque.doc.pdf}
-\insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/4longBlair.docx.pdf}
+\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
+\insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
+\insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
+\insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
+\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/6longCacean.docx.pdf}
+\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
+\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/8longCorredor.docx.pdf}
+\insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
+\insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
+\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
+\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/12longHannkenilljes.docx.pdf}
+\insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
+\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/14longHoffmann.doc.pdf}
+\insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
+\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
+\insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
+\insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
+\insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
+\insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
 \insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H.
-Reijven}{pdfs/long/5longBodlović.doc.pdf}
-\insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/6longCacean.docx.pdf}
-\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/7longCastro.doc.pdf}
-\insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/8longCorredor.docx.pdf}
-\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Gabor Zemplen}{pdfs/long/9longFreeman.doc.pdf}
+Reijven}{pdfs/long/22longReijven.doc.pdf}
+\insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
+\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/24longSinclair.doc.pdf}
+\insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
+\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Gabor Zemplen}{pdfs/long/27longZemplen.doc.pdf}
 

### 2020-03-25 eca2019proceedings.tex
voorwerk

@@
 
-\section*{Committees}
-	\addcontentsline{toc}{chapter}{Committees}
-	\subsection*{General chairs}
-	\begin{compactitem}[]
-	\item[] Bart Verheij
-	\item[] Marco Wiering
-	\end{compactitem}
-
-	\subsection*{Contact \& administration}
-	\begin{compactitem}[]
-	\item[] Elina Sietsema
-	\item[] Carlijne de Vries
-	\item[] Sarah van Wouwe
-	\end{compactitem}
-
-	\subsection*{Local organisation}
-	\begin{compactitem}[]
-		\item[] Luca Bandelli
-		\item[] Abe Brandsma
-		\item[] Tomasz Darmetko
-		\item[] Mingcheng Ding
-		\item[] Ana Dugeniuc
-		\item[] Joel During
-		\item[] Ameer Islam
-		\item[] Siebert Looije
-		\item[] Ren\'e Mellema
-		\item[] Michaela Mr\`azkov\'a
-		\item[] Annet Onnes
-		\item[] Benjamin Shafrey
-		\item[] Sjaak ten Caat
-		\item[] Albert Thie
-		\item[] Jelmer van der Linde
-		\item[] Luuk van Keeken
-		\item[] Paul Veldhuyzen
-		\item[] Randy Wind
-		\item[] Galiya Yeshmagambetova
-	\end{compactitem}
-
-	\subsection*{Program committee}
-	\begin{compactitem}[]
-		\item[] Stylianos Asteriadis, Maastricht University
-		\item[] Reyhan Aydogan, Delft University of Technology
-		\item[] Floris Bex, Utrecht University
-		\item[] Michael Biehl, University of Groningen
-		\item[] Mauro Birattari, Universit\'e Libre de Bruxelles
-		\item[] Hendrik Blockeel, Katholieke Universiteit Leuven
-		\item[] Hans L. Bodlaender, Utrecht University
-		\item[] Sander Bohte, Centrum Wiskunde \& Informatica (CWI)
-		\item[] Peter Bosman, Centrum Wiskunde \& Informatica (CWI)
-		\item[] Tibor Bosse, Vrije Universiteit Amsterdam
-		\item[] Bruno Bouzy, Paris Descartes University
-		\item[] Frances Brazier, Delft University of Technology
-		\item[] Bert Bredeweg, University of Amsterdam
-		\item[] Tristan Cazenave, Universit\'e Paris Dauphine
-		\item[] Tom Claassen, Radboud University Nijmegen
-		\item[] Walter Daelemans, University of Antwerp
-		\item[] Gregoire Danoy, University of Luxembourg
-		\item[] Mehdi Dastani, Utrecht University
-		\item[] Patrick De Causmaecker, Katholieke Universiteit Leuven
-		\item[] Martine De Cock, University of Washington Tacoma
-		\item[] Mathijs De Weerdt, Delft University of Technology
-		\item[] Beno\^it Depaire, Hasselt University
-		\item[] Frank Dignum, Utrecht University
-		\item[] Virginia Dignum, Delft University of Technology
-		\item[] Kurt Driessens, Maastricht University
-		\item[] Madalina Drugan, Technical University of Eindhoven
-		\item[] Sjur Dyrkolbotn, Western Norway University of Applied Sciences
-		\item[] Jason Farquhar, Radboud University Nijmegen
-		\item[] Ad Feelders, Utrecht University
-		\item[] Bart Goethals, University of Antwerp
-		\item[] Pascal Gribomont, University of Liège
-		\item[] Perry Groot, Radboud University Nijmegen
-		\item[] Marc Gyssens, Universiteit Hasselt
-		\item[] Frank Harmsen, Ernst \& Young Advisory
-		\item[] Maaike Harbers, Rotterdam University of Applied Sciences
-		\item[] Tom Heskes, Radboud University Nijmegen
-		\item[] Koen Hindriks, Delft University of Technology
-		\item[] Arjen Hommersom, Open University of the Netherlands
-		\item[] Mark Hoogendoorn, Vrije Universiteit Amsterdam
-		\item[] Gerda Janssens, Katholieke Universiteit Leuven
-		\item[] Maurits Kaptein, Eindhoven University of Technology
-		\item[] Uzay Kaymak, Eindhoven University of Technology
-		\item[] Walter Kosters, Leiden University
-		\item[] Johan Kwisthout, Radboud University Nijmegen
-		\item[] Tom Lenaerts, Université Libre de Bruxelles
-		\item[] Marco Loog, Delft University of Technology
-		\item[] Peter Lucas, Radboud University
-		\item[] Elena Marchiori, Radboud University Nijmegen
-		\item[] Wannes Meert, Katholieke Universiteit Leuven
-		\item[] John-Jules Meyer, Utrecht University
-		\item[] Peter Nov\'ak, Delft University of Technology
-		\item[] Ann Now\'e, Vrije Universiteit Brussel
-		\item[] Aske Plaat, Leiden University
-		\item[] Eric Postma, Tilburg University
-		\item[] Henry Prakken, University of Utrecht, University of Groningen
-		\item[] Jan Ramon, INRIA
-		\item[] Silja Renooij, Utrecht University
-		\item[] Nico Roos, Maastricht University
-		\item[] Stefan Schlobach, Vrije Universiteit Amsterdam
-		\item[] Pierre-Yves Schobbens, University of Namur
-		\item[] Johannes Scholtes, Maastricht University
-		\item[] Lambert Schomaker, University of Groningen
-		\item[] Martijn Schut, Universiteit van Amsterdam
-		\item[] Evgueni Smirnov, Maastricht University
-		\item[] Matthijs T. J. Spaan, Delft University of Technology
-		\item[] Gerasimos Spanakis, Maastricht University
-		\item[] Jennifer Spenader, University of Groningen
-		\item[] Ida Sprinkhuizen-Kuyper, Radboud University Nijmegen
-		\item[] Thomas Stützle, Universit\'e Libre de Bruxelles
-		\item[] Johan Suykens, Katholieke Universiteit Leuven
-		\item[] Niels Taatgen, University of Groningen
-		\item[] Annette Ten Teije, Vrije Universiteit Amsterdam
-		\item[] Dirk Thierens, Utrecht University
-		\item[] Karl Tuyls, University of Liverpool
-		\item[] Antal van den Bosch, Radboud University Nijmegen
-		\item[] Egon L. van den Broek, Utrecht University
-		\item[] Jaap van den Herik, Leiden University
-		\item[] Linda van der Gaag, Utrecht University
-		\item[] Peter van der Putten, Leiden University, Pegasystems
-		\item[] Leon van der Torre, University of Luxembourg
-		\item[] Natalie van der Wal, Vrije Universiteit Amsterdam
-		\item[] Tim van Erven, Leiden University
-		\item[] Marcel van Gerven, Radboud University Nijmegen
-		\item[] Frank van Harmelen, Vrije Universiteit Amsterdam
-		\item[] Martijn van Otterlo, Vrije Universiteit Amsterdam
-		\item[] M. Birna van Riemsdijk, Delft University of Technology
-		\item[] Maarten van Someren, University of Amsterdam
-		\item[] Marieke van Vugt, University of Groningen
-		\item[] Menno van Zaanen, Tilburg University
-		\item[] Joaquin Vanschoren, Eindhoven University of Technology
-		\item[] Marina Velikova, Radboud University Nijmegen
-		\item[] Remco Veltkamp, Utrecht University
-		\item[] Joost Vennekens, Katholieke Universiteit Leuven
-		\item[] Katja Verbeeck, Technologiecampus Gent
-		\item[] Rineke Verbrugge, University of Groningen
-		\item[] Michel Verleysen, Universit\'e Catholique de Louvain
-		\item[] Sicco Verwer, Delft University of Technology
-		\item[] Arnoud Visser, Universiteit van Amsterdam
-		\item[] Willem Waegeman, Ghent University
-		\item[] Martijn Warnier, Delft University of Technology
-		\item[] Gerhard Weiss, Maastricht University
-		\item[] Floris Wiesman, Academic Medical Center Amsterdam
-		\item[] Jef Wijsen, University of Mons
-		\item[] Mark H. M. Winands, Maastricht University
-		\item[] Radboud Winkels, Universiteit van Amsterdam
-		\item[] Cees Witteveen, Delft University of Technology
-		\item[] Marcel Worring, University of Amsterdam
-		\item[] Yingqian Zhang, Eindhoven University of Technology
-	\end{compactitem}
-
-\include{preface}
+\include{prep}
 

### 2020-03-25 preface.tex
voorwerk

@@
 
-BNAIC is the annual Benelux Conference on Artificial Intelligence.
-In 2017, the 29\textsuperscript{th} edition of BNAIC is organized by the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), University of Groningen, under the auspices of the Benelux Association for Artificial Intelligence (BNVKI) and the Dutch Research School for Information and Knowledge Systems (SIKS).
+After two successful editions held in Lisbon in 2015 and Fribourg in 2017, ECA was hosted in 2019 by the Faculty of Philosophy of the University of Groningen, on 24-27 June 2019.
+These two volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.
+The European Conference on Argumentation (ECA) is a pan-European biennial initiative aiming to consolidate and advance various strands of research on argumentation and reasoning by gathering scholars from a range of disciplines.
+While based in Europe, ECA involves and encourages participation by argumentation scholars from all over the world; it welcomes submissions linked to argumentation studies in general, in addition to those tackling the conference theme.
+The 2019 Groningen edition focused on dissent.
+The goal was to inquire into the virtues and vices of dissent, criticism, disagreement, objections, and controversy in light of legitimizing policy decisions, justifying beliefs, proving theorems, defending standpoints, or strengthening informed consent.
+It is well known that dissent may hinder the cooperation and reciprocity required for reason-based deliberation and decision-making.
+But then again, dissent also produces the kind of scrutiny and criticism required for reliable and robust outcomes.
+How much dissent does an argumentative practice require?
+What kinds of dissent should we promote, or discourage?
+How to deal with dissent virtuously?
+How to exploit dissent in artificial arguers?
+How has dissent been conceptualized in the history of rhetoric, dialectic and logic?
+The papers in these two volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).
+The conference had 224 participants, and 188 papers were presented.
+These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation.
+The contents of these two volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
+The proceedings contain papers that were accepted based on abstract submissions; each submission was thoroughly evaluated by three reviewers of our scientific board—for a full list of ECA committees, see www.ecargument.org.
+Volume I gathers ??
+long papers and associated commentaries, together with ??
+papers presented in the ??
+thematic panels that were held during ECA2019.
+Volume II gathers ??
+regular papers that were presented during the conference.
+Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings.
+First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality.
+In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants.
+Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these two volumes, and assisted us throughout in the process of producing the Proceedings.
+The next edition of ECA will take place in Rome in 2021, and we look forward to seeing the ECA community gathering again for another successful event.
 
-BNAIC 2017 takes place in Het Kasteel, Melkweg 1, Groningen, The Netherlands, on Wednesday November 8 and Thursday November 9, 2017.
-BNAIC 2017 includes invited speakers, research presentations, posters, demonstrations, a deep learning workshop (organized by our sponsor NVIDIA) and a research and business session.
-
-The four BNAIC 2017 keynote speakers are:
-
-\begin{itemize}
-	\item 
-Marco Dorigo, Universit\'{e} Libre de Bruxelles\\
-\emph{Swarm Robotics: Current Research Directions at IRIDIA}
-
-	\item 
-Laurens van der Maaten, Facebook AI Research\\
-\emph{From Visual Recognition to Visual Understanding}
-
-	\item 
-Luc Steels, Institute for Advanced Studies (ICREA), Barcelona\\
-\emph{Digital Replicants and Mind-Uploading
-}
-
-	\item 
-Rineke Verbrugge, University of Groningen\\
-\emph{Recursive Theory of Mind: Between Logic and Cognition}
-\end{itemize}
-
-\noindent Three FACt talks (FACulty focusing on the FACts of Artificial Intelligence) are scheduled:
-
-\begin{itemize}
-	\item 
-Bert Bredeweg, Universiteit van Amsterdam\\
-\emph{Humanly AI: Creating smart people with AI}
-	\item Eric Postma, Tilburg University\\
-\emph{Towards Artificial Human-like Intelligence}
-	\item Geraint Wiggins, Queen Mary University of London/Vrije Universiteit Brussel\\
-\emph{Introducing Computational Creativity}
-\end{itemize}
-
-\noindent Authors were invited to submit papers on all aspects of Artificial Intelligence.
-This year we have received 68 submissions in total.
-Of the 30 submitted Type A regular papers, 11 (37\%) were accepted for oral presentation, and 14 (47\%) for poster presentation.
-5 (17\%) were rejected.
-Of the 19 submitted Type B compressed contributions, 17 (89\%) were accepted for oral presentation, and 2 (11\%) for poster presentation.
-None were rejected.
-All 6 submitted Type C demonstration abstracts were accepted.
-Of the submitted 13 Type D thesis abstracts, 5 (38\%) were accepted for oral presentation, and 8 (62\%) for poster presentation.
-None were rejected.
-The selection was made using peer review.
-Each submission was assigned to three members of the program committee, and their expert reviews were the basis for our decisions.
-
-All submissions accepted for oral or poster presentations and all demonstration abstracts appear in the electronic preproceedings, made available on the conference web site during the conference (\url{http://bnaic2017.ai.rug.nl/}).
-All 11 Type A regular papers accepted for oral presentation will appear in the postproceedings, to be published in the Springer CCIS series after the conference.
-
-The BNAIC 2017 conference would not be possible without the support and efforts of many. We thank the members of the program committee for their constructive and scholarly reviews. We are grateful to 
-    Elina Sietsema, Carlijne de Vries and 
-		Sarah van Wouwe, members of the administrative staff at the Institute of Artificial Intelligence and Cognitive Engineering (ALICE), for their tireless and reliable support.
-We thank our local organisation team
-		Luca Bandelli,
-    Abe Brandsma,
-    Tomasz Darmetko,
-    Mingcheng Ding,
-    Ana Dugeniuc,
-    Joel During,
-    Ameer Islam,
-    Siebert Looije,
-    Ren\'{e} Mellema,
-    Michaela Mr\'{a}zkov\'{a},
-    Annet Onnes,
-    Benjamin Shaffrey,
-    Sjaak ten Caat,
-    Albert Thie,
-    Jelmer van der Linde,
-    Luuk van Keeken,
-    Paul Veldhuyzen,
-    Randy Wind, and
-    Galiya Yeshmagambetova, 
-all students in our BSc and MSc Artificial Intelligence programs, for enthusiastically volunteering to help out in many ways.
-We thank Annet Onnes for preparing the preproceedings, Jelmer van der Linde for developing the web site, Randy Wind for designing the program leaflet, and Albert Thie for coordinating the local organisation.
-
-We are grateful to our sponsors for their generous support of the conference:
-\begin{itemize}
-%		
-	\item 
-Target Holding
-	\item 
-NVIDIA Deep Learning Institute
-%
-	\item 
-Anchormen
-	\item 
-Quint
-	\item 
-the Netherlands Research School for Information and Knowledge Systems (SIKS)
-	\item 
-SIM-CI
-%
-	\item 
-Textkernel
-	\item 
-LuxAI
-	\item 
-IOS Press
-	\item 
-Stichting Knowledge-Based Systems (SKBS)
-	\item 
-SSN Adaptive Intelligence 
-\end{itemize}
-
-\noindent 
-We wish you a pleasant conference!
-
-\begin{flushright}
-Bart Verheij \& Marco Wiering
-\end{flushright}
+Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar, Bart Verheij

### 2020-03-25 prep.tex
prep.tex

\newpage
\begin{center}
Studies in Logic\\
Logic and Argumentation\\
Volume ?
\vspace{10cm}

Reason to Dissent\\
Proceedings of the 3rd European Conference on Argumentation\\
Volume I
\end{center}

\newpage

\newpage

\begin{center}
Reason to Dissent\\
Proceedings of the 3rd European Conference on Argumentation\\
Volume II
\vspace{10cm}

Edited by\\
Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar and Bart Verheij
\end{center}

\newpage

Copyright things?

\newpage

\include{preface}

\section*{Conference Organization}
	\addcontentsline{toc}{chapter}{Conference Organization}
	\subsection*{Organising committee}
	\begin{compactitem}[]
	\item[] Jan Albert Van Laar, chair (University of Groningen)
	\item[] Henrike Jansen (University of Leiden)
	\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
	\item[] Bart Verheij (University of Groningen)
	\end{compactitem}

	\subsection*{Programme committee}
	\begin{compactitem}[]
	\item[] Dale Hample, chair (University of Maryland)
	\item[] Henrike Jansen, secretary (University of Leiden)
	\item[] Marcin Lewinski (Universidade Nova de Lisboa)
	\item[] Frank Zenker (Universität Konstanz, Slovak Academy of Sciences, Lund University)
	\item[] Juho Ritola (University of Turku)
 	\end{compactitem}

 	\subsection*{ECA steering committee}
 	\begin{compactitem}[]
	\item[] Fabio Paglieri, chair (ISTC-CNR, Rome, Italy)
	\item[] Jan Albert Van Laar, deputy chair (University of Groningen, The Netherlands)
	\item[] Lilian Bermejo Luque (University of Granada, Spain)
	\item[] Katarzyna Budzyńska (Polish Academy of Sciences, Poland)
	\item[] Henrike Jansen (University of Leiden, The Netherlands)
	\item[] Marcin Koszowy (University of Białystok, Poland)
	\item[] Marcin Lewiński (Universidade Nova de Lisboa, Portugal)
	\item[] Dima Mohammed (Universidade Nova de Lisboa, Portugal)
	\item[] Steve Oswald (University of Fribourg, Switzerland)
	\item[] Juho Ritola (University of Turku, Finland)
	\item[]Sara Rubinelli (University of Lucerne, Switzerland)
	\item[] Frank Zenker (University of Lund, Sweden)
	\end{compactitem}

	\subsection*{Scientific Panel}
	\begin{compactitem}[]
		\item[] Adam Richards
		\item[] Alessandra Von Burg, Wake Forest University
		\item[] Amy Johnson
		\item[] Andrea Rocci, Università della Svizzera Italiana
		\item[] Andrei Moldovan, University of Salamanca
		\item[] Andrew Aberdein, Florida Institute of Technology
		\item[] Assimakis Tseronis, Örebro University
		\item[] Bart Garssen, University of Amsterdam
		\item[] Bart van Klink, Vrije Universiteit Amsterdam
		\item[] Beth Innocenti, University of Kansas
		\item[] Carly Woods, University of Maryland
		\item[] Catherine Hundleby, University of Windsor
		\item[] Christoph Lumer, University of Siena
		\item[] Christopher Tindale, University of Windsor
		\item[] Constanza Ihnen, University of Chile, Law Faculty, Institute of Argumentation
		\item[] Corina Andone, University of Amsterdam
		\item[] Daniel Cohen
		\item[] David Godden, Michigan State University
		\item[] David Hitchcock, McMaster University
		\item[] David Williams, Florida Atlantic University
		\item[] David Zarefsky, Northwestern University
		\item[] Eveline Feteris, University of Amsterdam
		\item[] Fabrizio Macagno, Universidade NOVA de Lisboa
		\item[] Floriana Grasso, University of Liverpool
		\item[] Francisca Snoeck Henkemans, University of Amsterdam
		\item[] C. Goddu, University of Richmond
		\item[] Gabor Zemplen, Budapest University of Technology and Economics
		\item[] Gabrijela Kisicek, University of Zagreb
		\item[] Gilbert Plumer, Law School Admission Council (retired)
		\item[] Gregor Betz, KIT Karlsruhe
		\item[] Hans Hoeken, Utrecht University
		\item[] Hans Vilhelm Hansen, University of Windsor
		\item[] Harald Wohlrapp,
		\item[] Harry Weger, University of Central Florida
		\item[] Harvey Siegel, University of Miami
		\item[] Hen Jans, Univ Leiden
		\item[] Henry Prakken, Department of Information and Computing Sciences, University of Utrecht \& Faculty of Law, University of Groningen
		\item[] Igor Z. Zagar, Educational Research Institute
		\item[] Ingeborg van der Geest, University of Amsterdam
		\item[] Isabela Fairclough, University of Cantral Lancashire
		\item[] Anthony Blair, University of Windsor
		\item[] Jacky Visser, University of Dundee
		\item[] Jean Goodwin
		\item[] Jérôme Jacquin, University of Lausanne
		\item[] Joana Garmendia, ILCLI (University of the Basque Country)
		\item[] John Casey, Northeastern Illinois University
		\item[] Jos Hornikx, Radboud University
		\item[] Juho Ritola, University of Helsinki
		\item[] Katharina Stevens, University of Lethbridge
		\item[] Laura Vincze, Dpt of Linguistics, Pisa
		\item[] Lena Wahlberg, Lund University
		\item[] Leo Groarke, Trent University
		\item[] Lotte Van Poppel, University of Amsterdam
		\item[] Louis De Saussure, University of Neuchatel
		\item[] Maarten van Leeuwen, Leiden University Centre for Linguistics (LUCL)
		\item[] Manfred Kienpointner, University of Innsbruck
		\item[] Manfred Kraus, University of Tübingen
		\item[] Manfred Stede, Univ Potsdam
		\item[] Marianne Doury, Paris Descartes University
		\item[] Mariusz Urbanski, Adam Mickiewicz University
		\item[] Mark Aakhus, Rutgers University
		\item[] Marta Zampa, Zurich University of Applied Sciences
		\item[] Martin Hinton, University of Lodz
		\item[] Martin Reisigl, University of Bern
		\item[] Mehmet Ali Uzelgun, Universidade NOVA de Lisboa
		\item[] Michael Baumtrog, Ryerson University
		\item[] Michael Hoffmann, Georgia Institute of Technology
		\item[] Michael Hoppmann, Northeastern University
		\item[] Michel Dufour, Université Sorbonne-Nouvelle
		\item[] Minghui Xiong, Institute of Logic and Cognition, Sun Yat-sen University
		\item[] Niki Pfeifer, Munich Center for Mathematical Philosophy
		\item[] Patrick Bondy, Cornell University
		\item[] Paula Olmos,
		\item[] Rudi Palmieri, University of Liverpool
		\item[] Ruth Amossy, Tel-Aviv University
		\item[] Sara Greco, Università della Svizzera italiana
		\item[] Sarah Bigi, Università Cattolica del Sacro Cuore
		\item[] Scott Aikin, Vanderbilt University
		\item[] Steven Patterson, Marygrove College
		\item[] Susan Kline, The Ohio State University
		\item[] Thierry Herman, Universities of Neuchatel and lausanne
		\item[] Yun Xie, Sun Yat-sen Univ.
	\end{compactitem}

\newpage

\section*{Keynote Speakers}
	\addcontentsline{toc}{chapter}{Keynote Speakers}
\subsection*{Critical thinking as discourse}
\emph{Deanna Kuhn}
\\\\
Less than it is an individual ability or skill, critical thinking is a dialogic practice people engage in and commit to, initially interactively and then in interiorized form with the other only implicit. An argument depends for its meaning on how others respond (Gergen, 2015). In advancing arguments, well-practiced thinkers anticipate their defeasibility as a consequence of others’ objections, in addition envisioning their own potential rebuttals. Whether in external or interiorized form, the dialogic process creates something new, while itself undergoing development.

This perspective may be useful in sharpening definition of the construct of critical thinking and in so doing help to bring together the largely separate strands of work examining it as a theoretical construct, a measurable skill, and an educational objective. Implications for education follow. How might critical thinking as a shared practice be engaged in within educational settings in ways that will best support its development? One step is to privilege frequent practice of direct peer-to-peer discourse. A second is to take advantage of the leveraging power of dialog as a bridge to individual argument – one affording students’ argumentative writing a well-envisioned audience and purpose. Illustrations of this bridging power are presented.   Finally, implications for assessment of critical thinking are noted and a case made for the value of people’s committing to a high standard of critical thinking as a shared and interactive practice.

\subsection*{Revisiting Apologie de la polémique: about some “felicity conditions” allowing for coexistence in dissent}
\emph{Ruth Amossy}
\\\\
In my book entitled Apologie de la polémique (2014), I claimed that polemical discourse fulfils various social functions, among which “coexistence in dissensus” seems the most important. It means not only that disagreement is the basis of life in society, and the principle on which argumentation as a common, rational search for the reasonable, is built. It also signifies that agreement cannot always be reached in democratic societies recognizing the importance of diversity and difference, so that disagreement has to be managed through verbal confrontations, namely, agonistic discussions and polemical exchanges. It thus appears that the latter, though generally blamed for its radicalization and polarization, plays an important role in the public sphere. Among others, public polemics helps opposite parties to voice conflicting opinions and fight for antagonistic solutions without recurring to arms. To use Chantal Mouffe’s words, it transforms “enemies” to be destroyed into “adversaries” who have a right to speak. Beside other social functions discussed in the book, polemics authorizes what the French call a “vivre-ensemble” – the possibility for people who do not share the same opinions, if not the same premises, to share the same national space and live together without outbursts of violence.

However, the emphasis on dissent and its polemical management is not without raising multiple questions concerning the conditions of possibility and the limits of the so-called coexistence in dissent. Obviously, the use of polemical discourse is not enough to prevent citizens from physically fighting each other and even, sometimes, to dispel the specter of civil war. Outbursts of violence against refugees regularly occur in Germany where the polemical discussion is vivid. In France, the polemical exchanges on Emmanuel Macrons’ reforms and the authorized street demonstrations did not prevent urban violence. Even if polemical campaign discourse is tolerated, it did not prevent armed confrontations in certain African countries such as Ivory Coast. What, then, are the “felicity conditions” needed in order for public polemics to secure a peaceful “living together” in the framework of persistent and sometimes deep disagreements that can hardly be avoided in the democratic space? My contention is that to answer this question, it is necessary to explore polemical confrontations in their institutional framework, and to examine the functioning of polemical discourse in relation to the political, forensic and cultural factors that determine (at least partly) its degree of success. After synthetizing the finding of my first research into dissent and its polemical management, I will try – on the basis of a few case studies – to gather some of the “felicity conditions” necessary to make coexistence in dissent possible.

\subsection*{Dissent needed: argumentation for AI and law applications}
\emph{Katie Atkinson}
\\\\
As technological advances in artificial intelligence are being turned into deployed products, societal questions are being raised about the need for AI tools to be able to explain their decisions to humans.  This need becomes even more pressing when AI technologies are applied in domains where critical decisions are made that can result in a significant effect upon individuals or groups in society.  One such domain is law, where there is a thriving market developing in support tools for assisting with a variety of legal tasks carried out within law firms and the wider legal sector.  Law is a domain rich in argumentation and support tools that are used to aid legal decision making should similarly be able to explain why a particular outcome of a decision has been reached, and not an alternative outcome.  Dissent needs to be captured and revealed within AI reasoners to ensure that the decision space is explored from different perspectives, if AI tools are to be deployed effectively to assist with legal reasoning tasks.  In this talk I will discuss a body of work on computational models of argument for legal reasoning and show how dissent features within this work to promote scrutability of AI decision making.

% \newpage
% \pdfbookmark[chapter]{Table of Contents}{toc}
% \tableofcontents
% \newpage

 \pdfbookmark[chapter]{Preface}{preface}

\mainmatter
\MakePlainPagestyleEmpty

% \include{papers-with-names}

\backmatter

% \addcontentsline{toc}{chapter}{Index of Authors}
% \printindex[authors]

% \includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/back}

\end{document}

### 2020-03-26 page-formats.sh
Script to check page size

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+find pdfs -name "*.pdf" -print | while read FILE; do
+	echo -n $FILE ""
+	pdfinfo $FILE | grep Page\ size
+done

### 2020-03-26 papers.tex
Add pdfs to papers.tex

@@
+% TODO
+%  [ ] move each commentary directly after each long paper
+%  [ ] fill in titles of commentaries
+%  [ ] fill in full author for each commentary
+
 \part{Long papers}
@@
 
+% \part{Commentary}
+
+\insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
+\insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}
+
 % \addtocontents{toc}{\protect\newpage}
@@
 
+\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
+\insertmydocument{chapter}{Is there a crisis of dissent and disagreement in argument theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
+\insertmydocument{chapter}{Epistemic Tolerance}{Dominik Balg}{pdfs/regular/7regularBalg.doc.pdf} % 7
+\insertmydocument{chapter}{Structuring Controversy: The Dialectic of Disagreement}{Sharon Bailin, Mark Battersby}{pdfs/regular/8regularBailin.docx.pdf} % 8
+\insertmydocument{chapter}{The role of reasoning and arguing in youth democratic participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
+\insertmydocument{chapter}{Pictures and Reasoning: visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
+\insertmydocument{chapter}{Issues leading to argumentative discussions during family mealtime conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
+\insertmydocument{chapter}{Value-based argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
+\insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
+\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
+\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catalán}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
+\insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
+Cheng}{pdfs/regular/20regularCheng.docx.pdf} % 20
+\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens,  Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
+\insertmydocument{chapter}{The semantic mechanisms underlying disagreement. An argumentative semantics approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
+\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{Hédi Virág Csordás}{pdfs/regular/25regularCSORDÁS.doc.pdf} % 25
+\insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
+\insertmydocument{chapter}{Arguing Brexit on Twitter: a corpus linguistic study}{Natalie Dykes,  Philipp Heinrich,  Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
+\insertmydocument{chapter}{Protagoras’ principles, disagreement and the possibility of error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
+\insertmydocument{chapter}{Changing minds through argumentation: Black Pete as a case study}{Catarina Dutilh Novaes,  Emily Sullivan,  Thirza Lagewaard,  Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
+\insertmydocument{chapter}{The pragma-dialectical view of comparison argumentation}{Frans van Eemeren,  Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
+\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{Léa Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
+\insertmydocument{chapter}{The visual rhetoric of iconic photographs as topoi in editorial cartoons: an argumentative analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
+\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier,  Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
+\insertmydocument{chapter}{Representing second-order arguments with Adpositional Argumentation}{Federico Gobbo,  Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
+\insertmydocument{chapter}{Argumentation, dissent, and luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
+\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
+\insertmydocument{chapter}{Resolution of deep disagreement: not simply consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47
+\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
+\insertmydocument{chapter}{Towards a Theory of Informal Argument Semantics}{Martin Hinton}{pdfs/regular/49regularHinton.doc.pdf} % 49
+\insertmydocument{chapter}{Stereotyping}{David Hitchcock}{pdfs/regular/50regularHitchcock.doc.pdf} % 50
+\insertmydocument{chapter}{Changing Norms of Argumentation}{Beth Innocenti}{pdfs/regular/53regularInnocenti.doc.pdf} % 53
+\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
+\insertmydocument{chapter}{Formal specifications for dialogue games in multi-party healthcare coaching}{Mathilde Janier,  Alison Pease,  Mark Snaith,  Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
+\insertmydocument{chapter}{How courts should respond to the stories defendants tell: A Bayesian account of a Dutch ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
+\insertmydocument{chapter}{The spaces and places of argumentation: Developing a spatial model of argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
+\insertmydocument{chapter}{Aggressiveness as a qualifier of dissent in interpersonal arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
+\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Kišiček}{pdfs/regular/60regularKisicek.docx.pdf} % 60
+\insertmydocument{chapter}{Be reasonable! Ways to react to cases of presumed unreason}{Erik C. W. Krabbe,  Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
+\insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
+\insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
+\insertmydocument{chapter}{A decision tree for annotating argumentation scheme corpora}{John Lawrence,  Jacky Visser,  Douglas Walton,  Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71
+\insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
+\insertmydocument{chapter}{Strategic manoeuvring with the construction “We know that X” in parliamentary debates}{Matthijs Looij,  Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
+\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel López}{pdfs/regular/75regularLopez.doc.pdf} % 75
+\insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar,  Susan L.
+Kline}{pdfs/regular/78regularManohar.doc.pdf} % 78
+\insertmydocument{chapter}{Holism of reasons and its consequences for argumentation theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
+\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The text structure and discourse of disagreement in Irish letters to the editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81
+\insertmydocument{chapter}{An Argumentative Approach to the Justification of Abduction}{Paula Olmos}{pdfs/regular/86regularOlmos.doc.pdf} % 86
+\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: organ and tissue donation, public trust, the voice of dissent and informed consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
+\insertmydocument{chapter}{“The worst ever conceived by a man of genius.
+” Hume’s probability argument in A Treatise}{Jeanne Peijnenburg,  David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92
+\insertmydocument{chapter}{Character, Dog Whistles, and the Limits of Charity}{Kathryn Phillips}{pdfs/regular/94regularPhillips.doc.pdf} % 94
+\insertmydocument{chapter}{The rhetorical potential of metaphor: An experimental study on the effect of metaphors in argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
+\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. José Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
+\insertmydocument{chapter}{Can Literary Fiction be Suppositional Reasoning?}{Gilbert Plumer}{pdfs/regular/99regularPlumer.doc.pdf} % 99
+\insertmydocument{chapter}{Conspiracy Theories and Reasonable Disagreement}{Juho Ritola}{pdfs/regular/106regularRitola.doc.pdf} % 106
+\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristián Santibáñez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107
+\insertmydocument{chapter}{Beyond Randomized Clinical Trials: Emerging Innovations in Reasoning About Health}{Jodi Schneider,  Sally Jackson}{pdfs/regular/109regularSchneider.docx.pdf} % 109
+\insertmydocument{chapter}{Multimodal argumentation and dissent – a perspective of multimodal critical discourse analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111
+\insertmydocument{chapter}{Analogical Argumentation in Philosophical Thought Experiments}{Stefan Sleeuw}{pdfs/regular/112regularSleeuw.docx.pdf} % 112
+\insertmydocument{chapter}{Detecting and handling disagreement in multi-party health coaching}{Mark Snaith,  Alison Pease,  Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
+\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen,  Marko Tešić}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
+\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton,  Alice Toniolo}{pdfs/regular/118regularToniolo.doc.pdf} % 118
+\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fernández Walker,  Ana María Mora-Márquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
+\insertmydocument{chapter}{Conductive Arguments. Towards a solution of the riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
+\insertmydocument{chapter}{A ludological perspective on the shape of argument: Collaborative assent to dissenting opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
+\insertmydocument{chapter}{Towards the justification of warrant in a legal hard case: How to justify a legal rule by the backing}{Shiyang Yu,  Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127
+\insertmydocument{chapter}{How Should We Classify Argument Schemes?}{David Zarefsky}{pdfs/regular/129regularZarefsky.doc.pdf} % 129
+
 \part{Thematic papers}
+
+\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
+\insertmydocument{chapter}{The prospects for multimodal schemes of argument: Assessing Adbusters’ spoofing strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
+\insertmydocument{chapter}{(Mis)framing photographs as an obstacle to fair dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
+\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
+\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
+\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
+\insertmydocument{chapter}{Five approaches to argument strength: probabilistic, dialectical, structural, empirical, and computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
+\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
+\insertmydocument{chapter}{From dialogic to argument-based teaching: Significant teacher moves in framing classroom-based argumentation dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

### 2020-03-26 papers.tex
Don't end document early

@@
 
-\insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
-\insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}
 

### 2020-03-26 papers.tex
Fix a couple of filenames

@@
 % \insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascón-C.doc.pdf}
+% \insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
 % \insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
@@
 \insertmydocument{chapter}{The semantic mechanisms underlying disagreement. An argumentative semantics approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
-\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{Hédi Virág Csordás}{pdfs/regular/25regularCSORDÁS.doc.pdf} % 25
+\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{Hédi Virág Csordás}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
 \insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26

### 2020-03-31 authors.py
Don't break when run with Python 3

@@ -33,12 +33,12 @@ if __name__ == '__main__':
 		match = pattern.match(line)
 		if match:
 			for author in parse_authors(match.group('authors')):
-				print('\index[authors]{{{0}, {1}}}'.format(*author))
-			print('\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
+				print(r'\index[authors]{{{0}, {1}}}'.format(*author))
+			print(r'\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
 				section=match.group('title'),
 				id=parse_filename(match.group('file'))))
 		print(line)
 		if match:
 			print("")
 		
-	print("Done! Don't forget to enable imakeidx:\n  \usepackage{imakeidx}\n  \makeindex[name=authors,title=Index of Authors,options=-r]", file=sys.stderr)
+	print(r"Done! Don't forget to enable imakeidx:\n  \usepackage{imakeidx}\n  \makeindex[name=authors,title=Index of Authors,options=-r]", file=sys.stderr)

### 2020-03-31 papers.tex
Remove dead spaces etc
Fix most of the names to the point it compiles

@@
 % [ ] fill in full author for each commentary
+% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)
 
@@
 \insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
-\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catalán}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
+\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
 \insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
@@
 \insertmydocument{chapter}{The semantic mechanisms underlying disagreement. An argumentative semantics approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
-\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{Hédi Virág Csordás}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
+\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
 \insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
@@
 \insertmydocument{chapter}{The pragma-dialectical view of comparison argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
-\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{Léa Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
+\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
 \insertmydocument{chapter}{The visual rhetoric of iconic photographs as topoi in editorial cartoons: an argumentative analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
@@
 \insertmydocument{chapter}{Aggressiveness as a qualifier of dissent in interpersonal arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Kišiček}{pdfs/regular/60regularKisicek.docx.pdf} % 60
+\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
 \insertmydocument{chapter}{Be reasonable! Ways to react to cases of presumed unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
@@
 \insertmydocument{chapter}{Strategic manoeuvring with the construction “We know that X” in parliamentary debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel López}{pdfs/regular/75regularLopez.doc.pdf} % 75
+\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
 \insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.
@@
 \insertmydocument{chapter}{The rhetorical potential of metaphor: An experimental study on the effect of metaphors in argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
-\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. José Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
+\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
 \insertmydocument{chapter}{Can Literary Fiction be Suppositional Reasoning?}{Gilbert Plumer}{pdfs/regular/99regularPlumer.doc.pdf} % 99
 \insertmydocument{chapter}{Conspiracy Theories and Reasonable Disagreement}{Juho Ritola}{pdfs/regular/106regularRitola.doc.pdf} % 106
-\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristián Santibáñez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107
+\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristi\'{a}n Santib\'{a}\~{n}ez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107
 \insertmydocument{chapter}{Beyond Randomized Clinical Trials: Emerging Innovations in Reasoning About Health}{Jodi Schneider, Sally Jackson}{pdfs/regular/109regularSchneider.docx.pdf} % 109
@@
 \insertmydocument{chapter}{Detecting and handling disagreement in multi-party health coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
-\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen,  Marko Tešić}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
+\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/regular/118regularToniolo.doc.pdf} % 118
-\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fernández Walker,  Ana María Mora-Márquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
+\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
 \insertmydocument{chapter}{Conductive Arguments. Towards a solution of the riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125

### 2020-03-31 authors.py
Better error handling and don't break on comments

@@ -3,13 +3,14 @@ from __future__ import print_function
 import re
 import sys
 
-pattern = re.compile(r'^\\insertmydocument\{chapter\}\{(?P<title>.+?)\}\{(?P<authors>.+?)\}\{(?P<file>.+?)\}$')
+pattern = re.compile(r'^\\insertmydocument\{chapter\}\{(?P<title>.+?)\}\{(?P<authors>.+?)\}\{(?P<file>.+?)\}(?P<comment>\s*%.*)?$')
 
 def parse_authors(authors):
 	try:
-		rest, last = authors.rsplit(' and ', 1)
-		rest = rest.split(', ')
-		return [parse_author(author) for author in (rest + [last])]
+		# rest, last = authors.rsplit(' and ', 1)
+		# rest = rest.split(', ')
+		# return [parse_author(author) for author in (rest + [last])]
+		return [parse_author(author) for author in authors.split(', ')]
 	except ValueError:
 		return [parse_author(authors)]
 
@@ -24,21 +25,28 @@ def parse_author(author):
 
 def parse_filename(filename):
 	match = re.match(r'pdfs/(?P<type>\w+)/(?P<id>\d+)', filename)
+	if not match:
+		raise ValueError("Could not parse {}".format(filename))
 	return match.group('type') + '-' + match.group('id')
 
 
 if __name__ == '__main__':
-	for line in sys.stdin:
-		line = line.rstrip()
-		match = pattern.match(line)
-		if match:
-			for author in parse_authors(match.group('authors')):
-				print(r'\index[authors]{{{0}, {1}}}'.format(*author))
-			print(r'\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
-				section=match.group('title'),
-				id=parse_filename(match.group('file'))))
-		print(line)
-		if match:
-			print("")
+	try:
+		for line in sys.stdin:
+			line = line.rstrip()
+			match = pattern.match(line)
+			if match:
+				for author in parse_authors(match.group('authors')):
+					print(r'\index[authors]{{{0}, {1}}}'.format(*author))
+				print(r'\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
+					section=match.group('title'),
+					id=parse_filename(match.group('file'))))
+			print(line)
+			if match:
+				print("")
[…]

### 2020-04-11 papers.tex
Add commentary papers

@@
 \insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
+
 \insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
+\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
+
 \insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
+\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural differences between practical and cognitive presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
+
 \insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/6longCacean.docx.pdf}
+\insertmydocument{chapter}{Commentary on Cacean’s Reliability of Argument Mapping}{Roosmaryn Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
+
 \insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
+\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
+
 \insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/8longCorredor.docx.pdf}
+\insertmydocument{chapter}{Dissent and Democracy -- Commentary on Corredor’s Democratic Legitimacy and Acts of Dissent}{David Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
+
 \insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
+\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
+
 \insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
+\insertmydocument{chapter}{Knowledge and the epistemic function of argumentation -- Commentary on Gasc\'{o}n's Where are dissent and reasons in epistemic justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
+
 \insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
+\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
+
 \insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/12longHannkenilljes.docx.pdf}
+
 \insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
+\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
+
 \insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/14longHoffmann.doc.pdf}
+
 \insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
+\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the problem of overexpressed premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
+
 \insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
+\insertmydocument{chapter}{A wanting analysis -- Commentary on S.
+Jackson, S.
+Jacobs, Y.
+Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R.
+Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
+
 \insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
+
 \insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
+\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
+
 \insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
+
 \insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
+
 \insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H.
 Reijven}{pdfs/long/22longReijven.doc.pdf}
+\insertmydocument{chapter}{Commentary on Reijven’s Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Beth Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
+
 \insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
+\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
+
 \insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/24longSinclair.doc.pdf}
+\insertmydocument{chapter}{Commentary on Sinclair’s Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate about Funding Prep}{Sally Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
+
 \insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
-\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Gabor Zemplen}{pdfs/long/27longZemplen.doc.pdf}
+\insertmydocument{chapter}{An optimistic perspective on deep disagreement?
+Commentary on Tindale’s Strange Fish: Belief and the roots of disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
 
-% \part{Commentary}
-
-% \insertmydocument{chapter}{TODO-TITLE}{Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
-% \insertmydocument{chapter}{TODO-TITLE}{Üzelgün}{pdfs/commentary/27longZemplen-C.doc.pdf}
+\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
+\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
 

### 2020-04-14 prep.tex
prep update
include
Don't end document early
Make affiliations consistent
(and find missing ones)

@@
 
-\include{preface}
-
 \section*{Conference Organization}
@@
 		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
-	\item[] Frank Zenker (Universität Konstanz, Slovak Academy of Sciences, Lund University)
+		\item[] Frank Zenker (Lund University)
 		\item[] Juho Ritola (University of Turku)
@@
  	\begin{compactitem}[]
-	\item[] Fabio Paglieri, chair (ISTC-CNR, Rome, Italy)
-	\item[] Jan Albert Van Laar, deputy chair (University of Groningen, The Netherlands)
-	\item[] Lilian Bermejo Luque (University of Granada, Spain)
-	\item[] Katarzyna Budzyńska (Polish Academy of Sciences, Poland)
-	\item[] Henrike Jansen (University of Leiden, The Netherlands)
-	\item[] Marcin Koszowy (University of Białystok, Poland)
-	\item[] Marcin Lewiński (Universidade Nova de Lisboa, Portugal)
-	\item[] Dima Mohammed (Universidade Nova de Lisboa, Portugal)
-	\item[] Steve Oswald (University of Fribourg, Switzerland)
-	\item[] Juho Ritola (University of Turku, Finland)
-	\item[]Sara Rubinelli (University of Lucerne, Switzerland)
-	\item[] Frank Zenker (University of Lund, Sweden)
+		\item[] Fabio Paglieri, chair (ISTC-CNR)
+		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
+		\item[] Lilian Bermejo Luque (University of Granada)
+		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
+		\item[] Henrike Jansen (University of Leiden)
+		\item[] Marcin Koszowy (University of Białystok)
+		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
+		\item[] Dima Mohammed (Universidade Nova de Lisboa)
+		\item[] Steve Oswald (University of Fribourg)
+		\item[] Juho Ritola (University of Turku)
+		\item[]Sara Rubinelli (University of Lucerne)
+		\item[] Frank Zenker (University of Lund)
 	\end{compactitem}
@@
 	\begin{compactitem}[]
-		\item[] Adam Richards
-		\item[] Alessandra Von Burg, Wake Forest University
-		\item[] Amy Johnson
-		\item[] Andrea Rocci, Università della Svizzera Italiana
-		\item[] Andrei Moldovan, University of Salamanca
-		\item[] Andrew Aberdein, Florida Institute of Technology
-		\item[] Assimakis Tseronis, Örebro University
-		\item[] Bart Garssen, University of Amsterdam
-		\item[] Bart van Klink, Vrije Universiteit Amsterdam
-		\item[] Beth Innocenti, University of Kansas
-		\item[] Carly Woods, University of Maryland
-		\item[] Catherine Hundleby, University of Windsor
-		\item[] Christoph Lumer, University of Siena
-		\item[] Christopher Tindale, University of Windsor
-		\item[] Constanza Ihnen, University of Chile, Law Faculty, Institute of Argumentation
-		\item[] Corina Andone, University of Amsterdam
-		\item[] Daniel Cohen
-		\item[] David Godden, Michigan State University
-		\item[] David Hitchcock, McMaster University
-		\item[] David Williams, Florida Atlantic University
-		\item[] David Zarefsky, Northwestern University
-		\item[] Eveline Feteris, University of Amsterdam
-		\item[] Fabrizio Macagno, Universidade NOVA de Lisboa
-		\item[] Floriana Grasso, University of Liverpool
-		\item[] Francisca Snoeck Henkemans, University of Amsterdam
-		\item[] C. Goddu, University of Richmond
-		\item[] Gabor Zemplen, Budapest University of Technology and Economics
-		\item[] Gabrijela Kisicek, University of Zagreb
-		\item[] Gilbert Plumer, Law School Admission Council (retired)
-		\item[] Gregor Betz, KIT Karlsruhe
-		\item[] Hans Hoeken, Utrecht University
-		\item[] Hans Vilhelm Hansen, University of Windsor
-		\item[] Harald Wohlrapp,
-		\item[] Harry Weger, University of Central Florida
-		\item[] Harvey Siegel, University of Miami
-		\item[] Hen Jans, Univ Leiden
-		\item[] Henry Prakken, Department of Information and Computing Sciences, University of Utrecht \& Faculty of Law, University of Groningen
-		\item[] Igor Z. Zagar, Educational Research Institute
-		\item[] Ingeborg van der Geest, University of Amsterdam
-		\item[] Isabela Fairclough, University of Cantral Lancashire
-		\item[] Anthony Blair, University of Windsor
-		\item[] Jacky Visser, University of Dundee
-		\item[] Jean Goodwin
-		\item[] Jérôme Jacquin, University of Lausanne
-		\item[] Joana Garmendia, ILCLI (University of the Basque Country)
-		\item[] John Casey, Northeastern Illinois University
-		\item[] Jos Hornikx, Radboud University
-		\item[] Juho Ritola, University of Helsinki
-		\item[] Katharina Stevens, University of Lethbridge
-		\item[] Laura Vincze, Dpt of Linguistics, Pisa
-		\item[] Lena Wahlberg, Lund University
-		\item[] Leo Groarke, Trent University
-		\item[] Lotte Van Poppel, University of Amsterdam
-		\item[] Louis De Saussure, University of Neuchatel
-		\item[] Maarten van Leeuwen, Leiden University Centre for Linguistics (LUCL)
-		\item[] Manfred Kienpointner, University of Innsbruck
-		\item[] Manfred Kraus, University of Tübingen
-		\item[] Manfred Stede, Univ Potsdam
-		\item[] Marianne Doury, Paris Descartes University
-		\item[] Mariusz Urbanski, Adam Mickiewicz University
-		\item[] Mark Aakhus, Rutgers University
-		\item[] Marta Zampa, Zurich University of Applied Sciences
-		\item[] Martin Hinton, University of Lodz
-		\item[] Martin Reisigl, University of Bern
-		\item[] Mehmet Ali Uzelgun, Universidade NOVA de Lisboa
-		\item[] Michael Baumtrog, Ryerson University
-		\item[] Michael Hoffmann, Georgia Institute of Technology
-		\item[] Michael Hoppmann, Northeastern University
-		\item[] Michel Dufour, Université Sorbonne-Nouvelle
-		\item[] Minghui Xiong, Institute of Logic and Cognition, Sun Yat-sen University
-		\item[] Niki Pfeifer, Munich Center for Mathematical Philosophy
-		\item[] Patrick Bondy, Cornell University
-		\item[] Paula Olmos,
-		\item[] Rudi Palmieri, University of Liverpool
-		\item[] Ruth Amossy, Tel-Aviv University
-		\item[] Sara Greco, Università della Svizzera italiana
-		\item[] Sarah Bigi, Università Cattolica del Sacro Cuore
-		\item[] Scott Aikin, Vanderbilt University
-		\item[] Steven Patterson, Marygrove College
-		\item[] Susan Kline, The Ohio State University
-		\item[] Thierry Herman, Universities of Neuchatel and lausanne
-		\item[] Yun Xie, Sun Yat-sen Univ.
+		\item[] Adam Richards (Texas Christian University)
+		\item[] Alessandra Von Burg (Wake Forest University)
+		\item[] Amy Johnson (University of Oklahoma)
+		\item[] Andrea Rocci (Università della Svizzera Italiana)
+		\item[] Andrei Moldovan (University of Salamanca)
+		\item[] Andrew Aberdein (Florida Institute of Technology)
+		\item[] Assimakis Tseronis (Örebro University)
+		\item[] Bart Garssen (University of Amsterdam)
+		\item[] Bart van Klink (Vrije Universiteit Amsterdam)
+		\item[] Beth Innocenti (University of Kansas)
+		\item[] Carly Woods (University of Maryland)
+		\item[] Catherine Hundleby (University of Windsor)
+		\item[] Christoph Lumer (University of Siena)
+		\item[] Christopher Tindale (University of Windsor)
+		\item[] Constanza Ihnen (University of Chile, Law Faculty, Institute of Argumentation)
+		\item[] Corina Andone (University of Amsterdam)
+		\item[] Daniel Cohen (Colby College)
+		\item[] David Godden (Michigan State University)
+		\item[] David Hitchcock (McMaster University)
+		\item[] David Williams (Florida Atlantic University)
+		\item[] David Zarefsky (Northwestern University)
+		\item[] Eveline Feteris (University of Amsterdam)
+		\item[] Fabrizio Macagno (Universidade NOVA de Lisboa)
+		\item[] Floriana Grasso (University of Liverpool)
+		\item[] Francisca Snoeck Henkemans (University of Amsterdam)
+		\item[] C. Goddu (University of Richmond)
+		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
+		\item[] Gabrijela Kisicek (University of Zagreb)
+		\item[] Gilbert Plumer (Law School Admission Council) (retired)
+		\item[] Gregor Betz (KIT Karlsruher)
+		\item[] Hans Hoeken (Utrecht University)
+		\item[] Hans Vilhelm Hansen (University of Windsor)
+		\item[] Harald Wohlrapp (Universität Hamburg)
+		\item[] Harry Weger (University of Central Florida)
+		\item[] Harvey Siegel (University of Miami)
+		\item[] Hen Jans (University of Leiden)
+		\item[] Henry Prakken (University of Groningen)
+		\item[] Igor Z. Zagar (Educational Research Institute)
+		\item[] Ingeborg van der Geest (University of Amsterdam)
+		\item[] Isabela Fairclough (University of Cantral Lancashire)
+		\item[] Anthony Blair (University of Windsor)
+		\item[] Jacky Visser (University of Dundee)
+		\item[] Jean Goodwin (North Carolina State University)
+		\item[] Jérôme Jacquin (University of Lausanne)
+		\item[] Joana Garmendia (University of the Basque Country)
+		\item[] John Casey (Northeastern Illinois University)
+		\item[] Jos Hornikx (Radboud University)
+		\item[] Juho Ritola (University of Helsinki)
+		\item[] Katharina Stevens (University of Lethbridge)
+		\item[] Laura Vincze (Universityt of Pisa)
+		\item[] Lena Wahlberg (Lund University)
+		\item[] Leo Groarke (Trent University)
+		\item[] Lotte Van Poppel (University of Amsterdam)
+		\item[] Louis De Saussure (University of Neuchatel)
+		\item[] Maarten van Leeuwen (Leiden University Centre for Linguistics) (LUCL)
+		\item[] Manfred Kienpointner (University of Innsbruck)
+		\item[] Manfred Kraus (University of Tübingen)
+		\item[] Manfred Stede (University of Potsdam)
+		\item[] Marianne Doury (Paris Descartes University)
+		\item[] Mariusz Urbanski (Adam Mickiewicz University)
+		\item[] Mark Aakhus (Rutgers University)
+		\item[] Marta Zampa (Zurich University of Applied Sciences)
+		\item[] Martin Hinton (University of Lodz)
+		\item[] Martin Reisigl (University of Bern)
+		\item[] Mehmet Ali Uzelgun (Universidade NOVA de Lisboa)
+		\item[] Michael Baumtrog (Ryerson University)
+		\item[] Michael Hoffmann (Georgia Institute of Technology)
+		\item[] Michael Hoppmann (Northeastern University)
+		\item[] Michel Dufour (Université Sorbonne-Nouvelle)
+		\item[] Minghui Xiong (Sun Yat-sen University)
+		\item[] Niki Pfeifer (Munich Center for Mathematical Philosophy)
+		\item[] Patrick Bondy (Cornell University)
+		\item[] Paula Olmos (Universidad Autónoma de Madrid)
+		\item[] Rudi Palmieri (University of Liverpool)
+		\item[] Ruth Amossy (Tel-Aviv University)
+		\item[] Sara Greco (Università della Svizzera Italiana)
+		\item[] Sarah Bigi (Università Cattolica del Sacro Cuore)
+		\item[] Scott Aikin (Vanderbilt University)
+		\item[] Steven Patterson (Marygrove College)
+		\item[] Susan Kline (The Ohio State University)
+		\item[] Thierry Herman (Universities of Neuchatel and lausanne)
+		\item[] Yun Xie (Sun Yat-sen University)
 	\end{compactitem}
@@
 In this talk I will discuss a body of work on computational models of argument for legal reasoning and show how dissent features within this work to promote scrutability of AI decision making.
-
-% \newpage
-% \pdfbookmark[chapter]{Table of Contents}{toc}
-% \tableofcontents
-% \newpage
-
- \pdfbookmark[chapter]{Preface}{preface}
-
-\mainmatter
-\MakePlainPagestyleEmpty
-
-% \include{papers-with-names}
-
-\backmatter
-
-% \addcontentsline{toc}{chapter}{Index of Authors}
-% \printindex[authors]
-
-% \includepdf[pages=1-,pagecommand={\thispagestyle{empty}}]{layout/back}
-
-\end{document}

### 2020-04-14 prep.tex
Sort by last name

@@
 	\begin{compactitem}[]
+		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
+		\item[] Henrike Jansen (University of Leiden)
 		\item[] Jan Albert Van Laar, chair (University of Groningen)
-		\item[] Henrike Jansen (University of Leiden)
-		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
 		\item[] Bart Verheij (University of Groningen)
@@
 		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
+		\item[] Juho Ritola (University of Turku)
 		\item[] Frank Zenker (Lund University)
-		\item[] Juho Ritola (University of Turku)
  	\end{compactitem}
@@
  	\begin{compactitem}[]
-		\item[] Fabio Paglieri, chair (ISTC-CNR)
-		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
 		\item[] Lilian Bermejo Luque (University of Granada)
@@
 		\item[] Marcin Koszowy (University of Białystok)
+		\item[] Jan Albert Van Laar, deputy chair (University of Groningen)
 		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
@@
 		\item[] Steve Oswald (University of Fribourg)
+		\item[] Fabio Paglieri, chair (ISTC-CNR)
 		\item[] Juho Ritola (University of Turku)
-		\item[]Sara Rubinelli (University of Lucerne)
+		\item[] Sara Rubinelli (University of Lucerne)
 		\item[] Frank Zenker (University of Lund)
@@
 	\begin{compactitem}[]
-		\item[] Adam Richards (Texas Christian University)
+		\item[] Mark Aakhus (Rutgers University)
+		\item[] Andrew Aberdein (Florida Institute of Technology)
+		\item[] Scott Aikin (Vanderbilt University)
+		\item[] Mehmet Ali Uzelgun (Universidade NOVA de Lisboa)
+		\item[] Ruth Amossy (Tel-Aviv University)
+		\item[] Corina Andone (University of Amsterdam)
+		\item[] Michael Baumtrog (Ryerson University)
+		\item[] Gregor Betz (KIT Karlsruher)
+		\item[] Sarah Bigi (Università Cattolica del Sacro Cuore)
+		\item[] Anthony Blair (University of Windsor)
+		\item[] Patrick Bondy (Cornell University)
 		\item[] Alessandra Von Burg (Wake Forest University)
-		\item[] Amy Johnson (University of Oklahoma)
-		\item[] Andrea Rocci (Università della Svizzera Italiana)
-		\item[] Andrei Moldovan (University of Salamanca)
-		\item[] Andrew Aberdein (Florida Institute of Technology)
-		\item[] Assimakis Tseronis (Örebro University)
+		\item[] John Casey (Northeastern Illinois University)
+		\item[] Daniel Cohen (Colby College)
+		\item[] Louis De Saussure (University of Neuchatel)
+		\item[] Marianne Doury (Paris Descartes University)
+		\item[] Michel Dufour (Université Sorbonne-Nouvelle)
+		\item[] Isabela Fairclough (University of Cantral Lancashire)
+		\item[] Eveline Feteris (University of Amsterdam)
+		\item[] Joana Garmendia (University of the Basque Country)
 		\item[] Bart Garssen (University of Amsterdam)
-		\item[] Bart van Klink (Vrije Universiteit Amsterdam)
-		\item[] Beth Innocenti (University of Kansas)
-		\item[] Carly Woods (University of Maryland)
-		\item[] Catherine Hundleby (University of Windsor)
-		\item[] Christoph Lumer (University of Siena)
-		\item[] Christopher Tindale (University of Windsor)
-		\item[] Constanza Ihnen (University of Chile, Law Faculty, Institute of Argumentation)
-		\item[] Corina Andone (University of Amsterdam)
-		\item[] Daniel Cohen (Colby College)
+		\item[] Ingeborg van der Geest (University of Amsterdam)
 		\item[] David Godden (Michigan State University)
+		\item[] C. Goddu (University of Richmond)
+		\item[] Jean Goodwin (North Carolina State University)
+		\item[] Floriana Grasso (University of Liverpool)
+		\item[] Sara Greco (Università della Svizzera Italiana)
+		\item[] Leo Groarke (Trent University)
+		\item[] Thierry Herman (Universities of Neuchatel and lausanne)
+		\item[] Martin Hinton (University of Lodz)
 		\item[] David Hitchcock (McMaster University)
-		\item[] David Williams (Florida Atlantic University)
-		\item[] David Zarefsky (Northwestern University)
-		\item[] Eveline Feteris (University of Amsterdam)
-		\item[] Fabrizio Macagno (Universidade NOVA de Lisboa)
-		\item[] Floriana Grasso (University of Liverpool)
-		\item[] Francisca Snoeck Henkemans (University of Amsterdam)
-		\item[] C. Goddu (University of Richmond)
-		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
-		\item[] Gabrijela Kisicek (University of Zagreb)
-		\item[] Gilbert Plumer (Law School Admission Council) (retired)
-		\item[] Gregor Betz (KIT Karlsruher)
 		\item[] Hans Hoeken (Utrecht University)
-		\item[] Hans Vilhelm Hansen (University of Windsor)
-		\item[] Harald Wohlrapp (Universität Hamburg)
-		\item[] Harry Weger (University of Central Florida)
-		\item[] Harvey Siegel (University of Miami)
-		\item[] Hen Jans (University of Leiden)
-		\item[] Henry Prakken (University of Groningen)
-		\item[] Igor Z. Zagar (Educational Research Institute)
-		\item[] Ingeborg van der Geest (University of Amsterdam)
-		\item[] Isabela Fairclough (University of Cantral Lancashire)
-		\item[] Anthony Blair (University of Windsor)
-		\item[] Jacky Visser (University of Dundee)
-		\item[] Jean Goodwin (North Carolina State University)
-		\item[] Jérôme Jacquin (University of Lausanne)
-		\item[] Joana Garmendia (University of the Basque Country)
-		\item[] John Casey (Northeastern Illinois University)
-		\item[] Jos Hornikx (Radboud University)
-		\item[] Juho Ritola (University of Helsinki)
-		\item[] Katharina Stevens (University of Lethbridge)
-		\item[] Laura Vincze (Universityt of Pisa)
-		\item[] Lena Wahlberg (Lund University)
-		\item[] Leo Groarke (Trent University)
-		\item[] Lotte Van Poppel (University of Amsterdam)
-		\item[] Louis De Saussure (University of Neuchatel)
-		\item[] Maarten van Leeuwen (Leiden University Centre for Linguistics) (LUCL)
-		\item[] Manfred Kienpointner (University of Innsbruck)
-		\item[] Manfred Kraus (University of Tübingen)
-		\item[] Manfred Stede (University of Potsdam)
-		\item[] Marianne Doury (Paris Descartes University)
-		\item[] Mariusz Urbanski (Adam Mickiewicz University)
-		\item[] Mark Aakhus (Rutgers University)
-		\item[] Marta Zampa (Zurich University of Applied Sciences)
-		\item[] Martin Hinton (University of Lodz)
-		\item[] Martin Reisigl (University of Bern)
-		\item[] Mehmet Ali Uzelgun (Universidade NOVA de Lisboa)
-		\item[] Michael Baumtrog (Ryerson University)
 		\item[] Michael Hoffmann (Georgia Institute of Technology)
 		\item[] Michael Hoppmann (Northeastern University)
-		\item[] Michel Dufour (Université Sorbonne-Nouvelle)
-		\item[] Minghui Xiong (Sun Yat-sen University)
-		\item[] Niki Pfeifer (Munich Center for Mathematical Philosophy)
-		\item[] Patrick Bondy (Cornell University)
+		\item[] Jos Hornikx (Radboud University)
+		\item[] Catherine Hundleby (University of Windsor)
+		\item[] Constanza Ihnen (University of Chile, Law Faculty, Institute of Argumentation)
+		\item[] Beth Innocenti (University of Kansas)
+		\item[] Jérôme Jacquin (University of Lausanne)
+		\item[] Henrike Jansen (University of Leiden)
+		\item[] Amy Johnson (University of Oklahoma)
+		\item[] Manfred Kienpointner (University of Innsbruck)
+		\item[] Gabrijela Kisicek (University of Zagreb)
+		\item[] Susan Kline (The Ohio State University)
+		\item[] Bart van Klink (Vrije Universiteit Amsterdam)
+		\item[] Manfred Kraus (University of Tübingen)
+		\item[] Maarten van Leeuwen (Leiden University)
+		\item[] Christoph Lumer (University of Siena)
+		\item[] Fabrizio Macagno (Universidade NOVA de Lisboa)
+		\item[] Andrei Moldovan (University of Salamanca)
 		\item[] Paula Olmos (Universidad Autónoma de Madrid)
 		\item[] Rudi Palmieri (University of Liverpool)
-		\item[] Ruth Amossy (Tel-Aviv University)
-		\item[] Sara Greco (Università della Svizzera Italiana)
-		\item[] Sarah Bigi (Università Cattolica del Sacro Cuore)
-		\item[] Scott Aikin (Vanderbilt University)
 		\item[] Steven Patterson (Marygrove College)
-		\item[] Susan Kline (The Ohio State University)
-		\item[] Thierry Herman (Universities of Neuchatel and lausanne)
+		\item[] Niki Pfeifer (Munich Center for Mathematical Philosophy)
+		\item[] Gilbert Plumer (Law School Admission Council) (retired)
+		\item[] Lotte van Poppel (University of Amsterdam)
+		\item[] Henry Prakken (University of Groningen)
+		\item[] Martin Reisigl (University of Bern)
+		\item[] Adam Richards (Texas Christian University)
+		\item[] Juho Ritola (University of Helsinki)
+		\item[] Andrea Rocci (Università della Svizzera Italiana)
+		\item[] Harvey Siegel (University of Miami)
+		\item[] Francisca Snoeck Henkemans (University of Amsterdam)
+		\item[] Manfred Stede (University of Potsdam)
+		\item[] Katharina Stevens (University of Lethbridge)
+		\item[] Christopher Tindale (University of Windsor)
+		\item[] Assimakis Tseronis (Örebro University)
+		\item[] Mariusz Urbanski (Adam Mickiewicz University)
+		\item[] Hans Vilhelm Hansen (University of Windsor)
+		\item[] Laura Vincze (Universityt of Pisa)
+		\item[] Jacky Visser (University of Dundee)
+		\item[] Lena Wahlberg (Lund University)
+		\item[] Harry Weger (University of Central Florida)
+		\item[] David Williams (Florida Atlantic University)
+		\item[] Harald Wohlrapp (Universität Hamburg)
+		\item[] Carly Woods (University of Maryland)
 		\item[] Yun Xie (Sun Yat-sen University)
+		\item[] Minghui Xiong (Sun Yat-sen University)
+		\item[] Igor Z. Zagar (Educational Research Institute)
+		\item[] Marta Zampa (Zurich University of Applied Sciences)
+		\item[] David Zarefsky (Northwestern University)
+		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
 	\end{compactitem}

### 2020-04-14 papers.tex
Capitalise All the Titles in the Table of Contents

@@
 \insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
-\insertmydocument{chapter}{What is wrong with deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
+\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
 
-\insertmydocument{chapter}{Is there an informal logic approach to argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
+\insertmydocument{chapter}{Is There an Informal Logic Approach to Argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
 \insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
 
-\insertmydocument{chapter}{Structural differences between practical and cognitive presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
-\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural differences between practical and cognitive presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
+\insertmydocument{chapter}{Structural Differences Between Practical and Cognitive Presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
+\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural Differences Between Practical and Cognitive Presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
 
@@
 
-\insertmydocument{chapter}{Strength of reasons for moral dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
+\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
 \insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
 
-\insertmydocument{chapter}{Where are dissent and reasons in epistemic justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
-\insertmydocument{chapter}{Knowledge and the epistemic function of argumentation -- Commentary on Gasc\'{o}n's Where are dissent and reasons in epistemic justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
+\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
+\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
 
@@
 
-\insertmydocument{chapter}{“’I said what I said’ - Black women and argumentative politeness norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
+\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
 \insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
@@
 
-\insertmydocument{chapter}{Grice, Machine Head and the problem of overexpressed premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
-\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the problem of overexpressed premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
+\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
+\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
 
@@
 
-\insertmydocument{chapter}{Speech act pluralism in argumentative polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
+\insertmydocument{chapter}{Speech Act Pluralism in Argumentative Polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
 
-\insertmydocument{chapter}{Evaluating relevance in analogical arguments through warrant-based reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
+\insertmydocument{chapter}{Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
 \insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
 
-\insertmydocument{chapter}{Arguments from expert opinion – An epistemological approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
+\insertmydocument{chapter}{Arguments From Expert Opinion – An Epistemological Approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
 
-\insertmydocument{chapter}{All-out attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
+\insertmydocument{chapter}{All-out Attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
 
@@
 
-\insertmydocument{chapter}{Disagreement, public reasoning, and (non-)authoritarian argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
+\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
 \insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
@@
 
-\insertmydocument{chapter}{Strange Fish: Belief and the roots of disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
+\insertmydocument{chapter}{Strange Fish: Belief and the Roots of Disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
 \insertmydocument{chapter}{An optimistic perspective on deep disagreement?
-Commentary on Tindale’s Strange Fish: Belief and the roots of disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
+Commentary on Tindale’s Strange Fish: Belief and the Roots of Disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
 
-\insertmydocument{chapter}{Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
-\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling dialogues: Multi-trait mapping of televised argumentative exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
+\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
+\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
 
@@
 \insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
-\insertmydocument{chapter}{Is there a crisis of dissent and disagreement in argument theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
+\insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
 \insertmydocument{chapter}{Epistemic Tolerance}{Dominik Balg}{pdfs/regular/7regularBalg.doc.pdf} % 7
 \insertmydocument{chapter}{Structuring Controversy: The Dialectic of Disagreement}{Sharon Bailin, Mark Battersby}{pdfs/regular/8regularBailin.docx.pdf} % 8
-\insertmydocument{chapter}{The role of reasoning and arguing in youth democratic participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
-\insertmydocument{chapter}{Pictures and Reasoning: visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
-\insertmydocument{chapter}{Issues leading to argumentative discussions during family mealtime conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
-\insertmydocument{chapter}{Value-based argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
+\insertmydocument{chapter}{The Role of Reasoning and Arguing in Youth Democratic Participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
+\insertmydocument{chapter}{Pictures and Reasoning: Visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
+\insertmydocument{chapter}{Issues Leading to Argumentative Discussions During Family Mealtime Conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
+\insertmydocument{chapter}{Value-based Argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
 \insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
 \insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
-\insertmydocument{chapter}{Relationships between narrative and argumentation. In defence of a functional account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
+\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
 \insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
@@
 \insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
-\insertmydocument{chapter}{The semantic mechanisms underlying disagreement. An argumentative semantics approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
+\insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
 \insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
 \insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
-\insertmydocument{chapter}{Arguing Brexit on Twitter: a corpus linguistic study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
-\insertmydocument{chapter}{Protagoras’ principles, disagreement and the possibility of error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
-\insertmydocument{chapter}{Changing minds through argumentation: Black Pete as a case study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
-\insertmydocument{chapter}{The pragma-dialectical view of comparison argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
-\insertmydocument{chapter}{An indexical characterization of disagreement based on possible worlds semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
-\insertmydocument{chapter}{The visual rhetoric of iconic photographs as topoi in editorial cartoons: an argumentative analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
+\insertmydocument{chapter}{Arguing Brexit on Twitter: A Corpus Linguistic Study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
+\insertmydocument{chapter}{Protagoras’ Principles, Disagreement and the Possibility of Error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
+\insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
+\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
+\insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
+\insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
 \insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
-\insertmydocument{chapter}{Representing second-order arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
-\insertmydocument{chapter}{Argumentation, dissent, and luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
+\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
+\insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
 \insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
-\insertmydocument{chapter}{Resolution of deep disagreement: not simply consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47
+\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47
 \insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
@@
 \insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
-\insertmydocument{chapter}{Formal specifications for dialogue games in multi-party healthcare coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
-\insertmydocument{chapter}{How courts should respond to the stories defendants tell: A Bayesian account of a Dutch ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
-\insertmydocument{chapter}{The spaces and places of argumentation: Developing a spatial model of argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
-\insertmydocument{chapter}{Aggressiveness as a qualifier of dissent in interpersonal arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
+\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
+\insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
+\insertmydocument{chapter}{The Spaces and Places of Argumentation: Developing a Spatial Model of Argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
+\insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
 \insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
-\insertmydocument{chapter}{Be reasonable! Ways to react to cases of presumed unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
+\insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
 \insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
 \insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
-\insertmydocument{chapter}{A decision tree for annotating argumentation scheme corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71
+\insertmydocument{chapter}{A Decision Tree for Annotating Argumentation Scheme Corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71
 \insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
-\insertmydocument{chapter}{Strategic manoeuvring with the construction “We know that X” in parliamentary debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, justification and inquiry: a pragmatist approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
+\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
+\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
 \insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.
 Kline}{pdfs/regular/78regularManohar.doc.pdf} % 78
-\insertmydocument{chapter}{Holism of reasons and its consequences for argumentation theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
-\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The text structure and discourse of disagreement in Irish letters to the editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81
+\insertmydocument{chapter}{Holism of Reasons and its Consequences for Argumentation Theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
+\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The Text Structure and Discourse of Disagreement in Irish letters to the Editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81
 \insertmydocument{chapter}{An Argumentative Approach to the Justification of Abduction}{Paula Olmos}{pdfs/regular/86regularOlmos.doc.pdf} % 86
-\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: organ and tissue donation, public trust, the voice of dissent and informed consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
+\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: Organ and Tissue Donation, Public Trust, the Voice of Dissent and Informed Consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
 \insertmydocument{chapter}{“The worst ever conceived by a man of genius.
-” Hume’s probability argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92
+” Hume’s Probability Argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92
 \insertmydocument{chapter}{Character, Dog Whistles, and the Limits of Charity}{Kathryn Phillips}{pdfs/regular/94regularPhillips.doc.pdf} % 94
-\insertmydocument{chapter}{The rhetorical potential of metaphor: An experimental study on the effect of metaphors in argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
-\insertmydocument{chapter}{Separate opinions as an argumentative activity type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
+\insertmydocument{chapter}{The Rhetorical Potential of Metaphor: An Experimental Study on the Effect of Metaphors in Argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
+\insertmydocument{chapter}{Separate Opinions as an Argumentative Activity Type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
 \insertmydocument{chapter}{Can Literary Fiction be Suppositional Reasoning?}{Gilbert Plumer}{pdfs/regular/99regularPlumer.doc.pdf} % 99
@@
 \insertmydocument{chapter}{Beyond Randomized Clinical Trials: Emerging Innovations in Reasoning About Health}{Jodi Schneider, Sally Jackson}{pdfs/regular/109regularSchneider.docx.pdf} % 109
-\insertmydocument{chapter}{Multimodal argumentation and dissent – a perspective of multimodal critical discourse analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111
+\insertmydocument{chapter}{Multimodal Argumentation and Dissent -- a Perspective of Multimodal Critical Discourse Analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111
 \insertmydocument{chapter}{Analogical Argumentation in Philosophical Thought Experiments}{Stefan Sleeuw}{pdfs/regular/112regularSleeuw.docx.pdf} % 112
-\insertmydocument{chapter}{Detecting and handling disagreement in multi-party health coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
-\insertmydocument{chapter}{Explaining away and the propensity interpretation of probability: the case of unequal priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
+\insertmydocument{chapter}{Detecting and Handling Disagreement in Multi-party Health Coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
+\insertmydocument{chapter}{Explaining Away and the Propensity Interpretation of Probability: the Case of Unequal Priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/regular/118regularToniolo.doc.pdf} % 118
-\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
-\insertmydocument{chapter}{Conductive Arguments. Towards a solution of the riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
-\insertmydocument{chapter}{A ludological perspective on the shape of argument: Collaborative assent to dissenting opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
-\insertmydocument{chapter}{Towards the justification of warrant in a legal hard case: How to justify a legal rule by the backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127
+\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval Reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
+\insertmydocument{chapter}{Conductive Arguments. Towards a Solution of the Riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
+\insertmydocument{chapter}{A Ludological Perspective on the Shape of Argument: Collaborative Assent to Dissenting Opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
+\insertmydocument{chapter}{Towards the Justification of Warrant in a Legal Hard Case: How to Justify a Legal Rule by the Backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127
 \insertmydocument{chapter}{How Should We Classify Argument Schemes?}{David Zarefsky}{pdfs/regular/129regularZarefsky.doc.pdf} % 129
@@
 \insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The prospects for multimodal schemes of argument: Assessing Adbusters’ spoofing strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
-\insertmydocument{chapter}{(Mis)framing photographs as an obstacle to fair dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
+\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
+\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
 \insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
@@
 \insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
-\insertmydocument{chapter}{Five approaches to argument strength: probabilistic, dialectical, structural, empirical, and computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
+\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
-\insertmydocument{chapter}{From dialogic to argument-based teaching: Significant teacher moves in framing classroom-based argumentation dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
+\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

### 2020-04-19 prep.tex
Affiliation for keynote speakers
frontmatter verkort en pagina nummers veranderd

@@
-\newpage
-\begin{center}
-Studies in Logic\\
-Logic and Argumentation\\
-Volume ?
-\vspace{10cm}
-
-Reason to Dissent\\
-Proceedings of the 3rd European Conference on Argumentation\\
-Volume I
-\end{center}
-
-\newpage
-
-\newpage
-
-\begin{center}
-Reason to Dissent\\
-Proceedings of the 3rd European Conference on Argumentation\\
-Volume II
-\vspace{10cm}
-
-Edited by\\
-Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar and Bart Verheij
-\end{center}
-
-\newpage
-
-Copyright things?
-
 \newpage
@@
 \subsection*{Critical thinking as discourse}
-\emph{Deanna Kuhn}
+\emph{Deanna Kuhn} -- \emph{Columbia University}
 \\\\
@@
 \subsection*{Revisiting Apologie de la polémique: about some “felicity conditions” allowing for coexistence in dissent}
-\emph{Ruth Amossy}
+\emph{Ruth Amossy} -- \emph{Tel-Aviv University}
 \\\\
@@
 \subsection*{Dissent needed: argumentation for AI and law applications}
-\emph{Katie Atkinson}
+\emph{Katie Atkinson} -- \emph{University of Liverpool}
 \\\\

### 2020-04-19 papers.tex
Move thematic papers up
Fix regular papers

@@
 
+\part{Thematic papers}
+
+\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
+\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
+\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
+\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
+\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
+\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
+\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
+\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
+\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
+
 % \addtocontents{toc}{\protect\newpage}
@@
 \insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
-\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47
+\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.docx.pdf} % 47
 \insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
@@
 \insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
-\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
+\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.docx.pdf} % 55
 \insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
@@
 \insertmydocument{chapter}{How Should We Classify Argument Schemes?}{David Zarefsky}{pdfs/regular/129regularZarefsky.doc.pdf} % 129
-
-\part{Thematic papers}
-
-\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
-\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
-\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
-\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
-\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
-\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
-\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
-\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

### 2020-04-19 papers.tex
Fix thematic papers

@@
 \insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
+\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
 \insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}

### 2020-04-19 papers-vol-1.tex
Split into two volumes

--- 2020-04-19 papers.tex
@@
-% TODO
-% [ ] move each commentary directly after each long paper
-% [ ] fill in titles of commentaries
-% [ ] fill in full author for each commentary
-% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)
-
 \part{Long papers}
@@
 \insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
-
-% \addtocontents{toc}{\protect\newpage}
-\part{Regular papers}
-
-\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
-\insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
-\insertmydocument{chapter}{Epistemic Tolerance}{Dominik Balg}{pdfs/regular/7regularBalg.doc.pdf} % 7
-\insertmydocument{chapter}{Structuring Controversy: The Dialectic of Disagreement}{Sharon Bailin, Mark Battersby}{pdfs/regular/8regularBailin.docx.pdf} % 8
-\insertmydocument{chapter}{The Role of Reasoning and Arguing in Youth Democratic Participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
-\insertmydocument{chapter}{Pictures and Reasoning: Visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
-\insertmydocument{chapter}{Issues Leading to Argumentative Discussions During Family Mealtime Conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
-\insertmydocument{chapter}{Value-based Argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
-\insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
-\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
-\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
-\insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
-Cheng}{pdfs/regular/20regularCheng.docx.pdf} % 20
-\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
-\insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
-\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
-\insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
-\insertmydocument{chapter}{Arguing Brexit on Twitter: A Corpus Linguistic Study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
-\insertmydocument{chapter}{Protagoras’ Principles, Disagreement and the Possibility of Error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
-\insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
-\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
-\insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
-\insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
-\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
-\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
-\insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
-\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
-\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.docx.pdf} % 47
-\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
-\insertmydocument{chapter}{Towards a Theory of Informal Argument Semantics}{Martin Hinton}{pdfs/regular/49regularHinton.doc.pdf} % 49
-\insertmydocument{chapter}{Stereotyping}{David Hitchcock}{pdfs/regular/50regularHitchcock.doc.pdf} % 50
-\insertmydocument{chapter}{Changing Norms of Argumentation}{Beth Innocenti}{pdfs/regular/53regularInnocenti.doc.pdf} % 53
-\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
-\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.docx.pdf} % 55
-\insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
-\insertmydocument{chapter}{The Spaces and Places of Argumentation: Developing a Spatial Model of Argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
-\insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
-\insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
-\insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
-\insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
-\insertmydocument{chapter}{A Decision Tree for Annotating Argumentation Scheme Corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71
-\insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
-\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
-\insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.
-Kline}{pdfs/regular/78regularManohar.doc.pdf} % 78
-\insertmydocument{chapter}{Holism of Reasons and its Consequences for Argumentation Theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
-\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The Text Structure and Discourse of Disagreement in Irish letters to the Editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81
-\insertmydocument{chapter}{An Argumentative Approach to the Justification of Abduction}{Paula Olmos}{pdfs/regular/86regularOlmos.doc.pdf} % 86
-\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: Organ and Tissue Donation, Public Trust, the Voice of Dissent and Informed Consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
-\insertmydocument{chapter}{“The worst ever conceived by a man of genius.
-” Hume’s Probability Argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92
-\insertmydocument{chapter}{Character, Dog Whistles, and the Limits of Charity}{Kathryn Phillips}{pdfs/regular/94regularPhillips.doc.pdf} % 94
-\insertmydocument{chapter}{The Rhetorical Potential of Metaphor: An Experimental Study on the Effect of Metaphors in Argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
-\insertmydocument{chapter}{Separate Opinions as an Argumentative Activity Type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
-\insertmydocument{chapter}{Can Literary Fiction be Suppositional Reasoning?}{Gilbert Plumer}{pdfs/regular/99regularPlumer.doc.pdf} % 99
-\insertmydocument{chapter}{Conspiracy Theories and Reasonable Disagreement}{Juho Ritola}{pdfs/regular/106regularRitola.doc.pdf} % 106
-\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristi\'{a}n Santib\'{a}\~{n}ez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107
-\insertmydocument{chapter}{Beyond Randomized Clinical Trials: Emerging Innovations in Reasoning About Health}{Jodi Schneider, Sally Jackson}{pdfs/regular/109regularSchneider.docx.pdf} % 109
-\insertmydocument{chapter}{Multimodal Argumentation and Dissent -- a Perspective of Multimodal Critical Discourse Analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111
-\insertmydocument{chapter}{Analogical Argumentation in Philosophical Thought Experiments}{Stefan Sleeuw}{pdfs/regular/112regularSleeuw.docx.pdf} % 112
-\insertmydocument{chapter}{Detecting and Handling Disagreement in Multi-party Health Coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
-\insertmydocument{chapter}{Explaining Away and the Propensity Interpretation of Probability: the Case of Unequal Priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
-\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/regular/118regularToniolo.doc.pdf} % 118
-\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval Reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
-\insertmydocument{chapter}{Conductive Arguments. Towards a Solution of the Riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
-\insertmydocument{chapter}{A Ludological Perspective on the Shape of Argument: Collaborative Assent to Dissenting Opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
-\insertmydocument{chapter}{Towards the Justification of Warrant in a Legal Hard Case: How to Justify a Legal Rule by the Backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127
-\insertmydocument{chapter}{How Should We Classify Argument Schemes?}{David Zarefsky}{pdfs/regular/129regularZarefsky.doc.pdf} % 129

### 2020-04-19 papers-vol-2.tex
Split into two volumes

--- 2020-04-19 papers.tex
@@
-% TODO
-% [ ] move each commentary directly after each long paper
-% [ ] fill in titles of commentaries
-% [ ] fill in full author for each commentary
-% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)
-
-\part{Long papers}
-
-\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
-\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
-
-\insertmydocument{chapter}{Is There an Informal Logic Approach to Argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
-\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
-
-\insertmydocument{chapter}{Structural Differences Between Practical and Cognitive Presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
-\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural Differences Between Practical and Cognitive Presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
-
-\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/6longCacean.docx.pdf}
-\insertmydocument{chapter}{Commentary on Cacean’s Reliability of Argument Mapping}{Roosmaryn Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
-
-\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
-\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
-
-\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/8longCorredor.docx.pdf}
-\insertmydocument{chapter}{Dissent and Democracy -- Commentary on Corredor’s Democratic Legitimacy and Acts of Dissent}{David Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
-
-\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
-\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
-
-\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
-\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
-
-\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
-\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
-
-\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/12longHannkenilljes.docx.pdf}
-
-\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
-\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
-
-\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/14longHoffmann.doc.pdf}
-
-\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
-\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
-
-\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
-\insertmydocument{chapter}{A wanting analysis -- Commentary on S.
-Jackson, S.
-Jacobs, Y.
-Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R.
-Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
-
-\insertmydocument{chapter}{Speech Act Pluralism in Argumentative Polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
-
-\insertmydocument{chapter}{Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
-\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
-
-\insertmydocument{chapter}{Arguments From Expert Opinion – An Epistemological Approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
-
-\insertmydocument{chapter}{All-out Attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
-
-\insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H.
-Reijven}{pdfs/long/22longReijven.doc.pdf}
-\insertmydocument{chapter}{Commentary on Reijven’s Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Beth Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
-
-\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
-\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
-
-\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/24longSinclair.doc.pdf}
-\insertmydocument{chapter}{Commentary on Sinclair’s Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate about Funding Prep}{Sally Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
-
-\insertmydocument{chapter}{Strange Fish: Belief and the Roots of Disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
-\insertmydocument{chapter}{An optimistic perspective on deep disagreement?
-Commentary on Tindale’s Strange Fish: Belief and the Roots of Disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
-
-\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
-\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
-
-\part{Thematic papers}
-
-\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.doc.pdf}
-\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
-\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
-\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
-\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
-\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
-\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
-\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
-
-% \addtocontents{toc}{\protect\newpage}
 \part{Regular papers}

### 2020-04-20 papers-vol-1.tex
Add keynote
updated titles vol 1

@@
 \insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
+
+\insertmydocument{chapter}{Revisiting Apologie de la Polémique: Coexistence in Dissent and its “Felicity Conditions”}{Ruth Amossy}{pdfs/keynote/1keynoteAmossy.doc.pdf}
+
 \insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
@@
 \insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
-\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
+\insertmydocument{chapter}{Comments on Diego Castro’s ``Critical Discussion in Sub-Optimal Settings''}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
 
@@
 \insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
-\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
+\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s ``Strength of Reasons for Moral Dissent''}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
 
 \insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
-\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
+\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's ``Where Are dissent and Reasons in Epistemic Justification?''}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
 
 \insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
-\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
+\insertmydocument{chapter}{Commentary on G. C. Goddu’s ``Justifying Questions?''}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
 
@@
 \insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
-\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
+\insertmydocument{chapter}{Commentary on Hoppmann’s ``Grice, Machine Head and the Problem of Overexpressed Premises''}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
 
@@
 Jacobs, Y.
-Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R.
+Zhang's ``Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference''}{Harald R.
 Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
@@
 
-\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
+\insertmydocument{chapter}{Visual Argument Schemes in the PTA}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
+\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry
+}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
 \insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
@@
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
-\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
+\insertmydocument{chapter}{From Dialogic to Argument-Based Teaching: Introducing Pragmatic Criteria to Analyse Whole-Class Interactions}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

### 2020-04-20 papers-vol-2.tex
updated titles vol 2

@@
 
-\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
+\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right (and Wrong)}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
 \insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
@@
 \insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
-\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
-\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
+\insertmydocument{chapter}{Conceptual Analysis of an Argumentation: using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
+\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation (AdArg)}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
 \insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
@@
 \insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
+\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse
+(An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
 \insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
@@
 \insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
-\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
+\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
 \insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

### 2020-04-20 papers-vol-1.tex
Fix names and some weird word/entry splitting issues

@@
 
-\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
+\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James B. Freeman}{pdfs/long/9longFreeman.doc.pdf}
 \insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s ``Strength of Reasons for Moral Dissent''}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
@@
 
-\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
+\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M. Henning}{pdfs/long/13longHenning.docx.pdf}
 \insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
@@
 \insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
-\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
+\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and\\(Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
 
@@
 
-\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
+\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A}. Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
 \insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
@@
 \insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
-\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
+\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, Kamila Debowska-Kozlowska, David Godden, Marcin Selinger, Simon Wells}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}

### 2020-04-20 papers-vol-2.tex
Fix names and some weird word/entry splitting issues

@@
 \insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
-\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
+\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel H. Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
 \insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
@@
 Cheng}{pdfs/regular/20regularCheng.docx.pdf} % 20
-\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
+\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel H. Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
 \insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
@@
 \insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
-\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
+\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans H. van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
 \insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
@@
 \insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation (AdArg)}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
+\addtocontents{toc}{\protect\newpage}
 \insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
-\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
+\insertmydocument{chapter}{Argument Scheme Theory}{Hans V. Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
 \insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.docx.pdf} % 47
@@
 \insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
+\addtocontents{toc}{\protect\newpage}
 \insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
@@
 \insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
+\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico E. L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
 \insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.

### 2020-05-04 authors.py
Fix sorting of names with non-ascii characters

@@ -2,6 +2,7 @@
 from __future__ import print_function
 import re
 import sys
+import locale
 
 pattern = re.compile(r'^\\insertmydocument\{chapter\}\{(?P<title>.+?)\}\{(?P<authors>.+?)\}\{(?P<file>.+?)\}(?P<comment>\s*%.*)?$')
 
@@ -30,6 +31,11 @@ def parse_filename(filename):
 	return match.group('type') + '-' + match.group('id')
 
 
+def sortable_str(latex):
+	plain_text = re.sub(r'\\.\{(.+?)\}', '\\1', latex)
+	return locale.strxfrm(plain_text)
+
+
 if __name__ == '__main__':
 	try:
 		for line in sys.stdin:
@@ -37,7 +43,7 @@ if __name__ == '__main__':
 			match = pattern.match(line)
 			if match:
 				for author in parse_authors(match.group('authors')):
-					print(r'\index[authors]{{{0}, {1}}}'.format(*author))
+					print(r'\index[authors]{{{1}@{0}}}'.format(', '.join(author), sortable_str(', '.join(author))))
 				print(r'\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
 					section=match.group('title'),
 					id=parse_filename(match.group('file'))))

### 2020-05-10 preface.tex
Don't end document early
Add paragraphs to preface
Fill in the numbers

@@
 \addcontentsline{toc}{chapter}{Preface}
+\pdfbookmark[chapter]{Preface}{preface}
 
@@
 These two volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.
+
 The European Conference on Argumentation (ECA) is a pan-European biennial initiative aiming to consolidate and advance various strands of research on argumentation and reasoning by gathering scholars from a range of disciplines.
@@
 The papers in these two volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).
+
 The conference had 224 participants, and 188 papers were presented.
@@
 The contents of these two volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
+
 The proceedings contain papers that were accepted based on abstract submissions; each submission was thoroughly evaluated by three reviewers of our scientific board—for a full list of ECA committees, see www.ecargument.org.
-Volume I gathers ??
-long papers and associated commentaries, together with ??
-papers presented in the ??
-thematic panels that were held during ECA2019.
-Volume II gathers ??
-regular papers that were presented during the conference.
+Volume I gathers 25 long papers and associated commentaries, together with 9 papers presented in the thematic panels that were held during ECA2019.
+Volume II gathers 67 regular papers that were presented during the conference.
+
 Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings.
@@
 Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these two volumes, and assisted us throughout in the process of producing the Proceedings.
+
 The next edition of ECA will take place in Rome in 2021, and we look forward to seeing the ECA community gathering again for another successful event.
 
-Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar, Bart Verheij
+\medskip
+
+\noindent Catarina Dutilh Novaes, Henrike Jansen, Jan Albert van Laar, Bart Verheij

### 2020-05-10 prep.tex
Add blank pages
Not really, LaTeX now does it for me! Because LaTeX is cool, unlike some other typesetting solution used during the compiling of these proceedings, a piece of software I am now so frustrated with that I'm fuming my frustrations in this commit message that no person should ever be reading. Seriously, are you trying to find dirt on me or something? If that's so, try reading my Twitter instead…
I think this is what Catarina meant with (chair)

@@
 		\item[] Henrike Jansen (University of Leiden)
-		\item[] Jan Albert Van Laar, chair (University of Groningen)
+		\item[] Jan Albert Van Laar (chair) (University of Groningen)
 		\item[] Bart Verheij (University of Groningen)
@@
 	\begin{compactitem}[]
-		\item[] Dale Hample, chair (University of Maryland)
-		\item[] Henrike Jansen, secretary (University of Leiden)
+		\item[] Dale Hample (chair) (University of Maryland)
+		\item[] Henrike Jansen (secretary) (University of Leiden)
 		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
@@
 		\item[] Marcin Koszowy (University of Białystok)
-		\item[] Jan Albert Van Laar, deputy chair (University of Groningen)
+		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
 		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
@@
 		\item[] Steve Oswald (University of Fribourg)
-		\item[] Fabio Paglieri, chair (ISTC-CNR)
+		\item[] Fabio Paglieri (chair) (ISTC-CNR)
 		\item[] Juho Ritola (University of Turku)
@@
 
-\newpage
+\cleardoublepage
 

### 2020-05-10 keynotes.tex
Move keynote after preface

--- 2020-04-19 prep.tex
@@
-\newpage
-
-\section*{Conference Organization}
-	\addcontentsline{toc}{chapter}{Conference Organization}
-	\subsection*{Organising committee}
-	\begin{compactitem}[]
-		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
-		\item[] Henrike Jansen (University of Leiden)
-		\item[] Jan Albert Van Laar, chair (University of Groningen)
-		\item[] Bart Verheij (University of Groningen)
-	\end{compactitem}
-
-	\subsection*{Programme committee}
-	\begin{compactitem}[]
-		\item[] Dale Hample, chair (University of Maryland)
-		\item[] Henrike Jansen, secretary (University of Leiden)
-		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
-		\item[] Juho Ritola (University of Turku)
-		\item[] Frank Zenker (Lund University)
- 	\end{compactitem}
-
- 	\subsection*{ECA steering committee}
- 	\begin{compactitem}[]
-		\item[] Lilian Bermejo Luque (University of Granada)
-		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
-		\item[] Henrike Jansen (University of Leiden)
-		\item[] Marcin Koszowy (University of Białystok)
-		\item[] Jan Albert Van Laar, deputy chair (University of Groningen)
-		\item[] Marcin Lewiński (Universidade Nova de Lisboa)
-		\item[] Dima Mohammed (Universidade Nova de Lisboa)
-		\item[] Steve Oswald (University of Fribourg)
-		\item[] Fabio Paglieri, chair (ISTC-CNR)
-		\item[] Juho Ritola (University of Turku)
-		\item[] Sara Rubinelli (University of Lucerne)
-		\item[] Frank Zenker (University of Lund)
-	\end{compactitem}
-
-	\subsection*{Scientific Panel}
-	\begin{compactitem}[]
-		\item[] Mark Aakhus (Rutgers University)
-		\item[] Andrew Aberdein (Florida Institute of Technology)
-		\item[] Scott Aikin (Vanderbilt University)
-		\item[] Mehmet Ali Uzelgun (Universidade NOVA de Lisboa)
-		\item[] Ruth Amossy (Tel-Aviv University)
-		\item[] Corina Andone (University of Amsterdam)
-		\item[] Michael Baumtrog (Ryerson University)
-		\item[] Gregor Betz (KIT Karlsruher)
-		\item[] Sarah Bigi (Università Cattolica del Sacro Cuore)
-		\item[] Anthony Blair (University of Windsor)
-		\item[] Patrick Bondy (Cornell University)
-		\item[] Alessandra Von Burg (Wake Forest University)
-		\item[] John Casey (Northeastern Illinois University)
-		\item[] Daniel Cohen (Colby College)
-		\item[] Louis De Saussure (University of Neuchatel)
-		\item[] Marianne Doury (Paris Descartes University)
-		\item[] Michel Dufour (Université Sorbonne-Nouvelle)
-		\item[] Isabela Fairclough (University of Cantral Lancashire)
-		\item[] Eveline Feteris (University of Amsterdam)
-		\item[] Joana Garmendia (University of the Basque Country)
-		\item[] Bart Garssen (University of Amsterdam)
-		\item[] Ingeborg van der Geest (University of Amsterdam)
-		\item[] David Godden (Michigan State University)
-		\item[] C. Goddu (University of Richmond)
-		\item[] Jean Goodwin (North Carolina State University)
-		\item[] Floriana Grasso (University of Liverpool)
-		\item[] Sara Greco (Università della Svizzera Italiana)
-		\item[] Leo Groarke (Trent University)
-		\item[] Thierry Herman (Universities of Neuchatel and lausanne)
-		\item[] Martin Hinton (University of Lodz)
-		\item[] David Hitchcock (McMaster University)
-		\item[] Hans Hoeken (Utrecht University)
-		\item[] Michael Hoffmann (Georgia Institute of Technology)
-		\item[] Michael Hoppmann (Northeastern University)
-		\item[] Jos Hornikx (Radboud University)
-		\item[] Catherine Hundleby (University of Windsor)
-		\item[] Constanza Ihnen (University of Chile, Law Faculty, Institute of Argumentation)
-		\item[] Beth Innocenti (University of Kansas)
-		\item[] Jérôme Jacquin (University of Lausanne)
-		\item[] Henrike Jansen (University of Leiden)
-		\item[] Amy Johnson (University of Oklahoma)
-		\item[] Manfred Kienpointner (University of Innsbruck)
-		\item[] Gabrijela Kisicek (University of Zagreb)
-		\item[] Susan Kline (The Ohio State University)
-		\item[] Bart van Klink (Vrije Universiteit Amsterdam)
-		\item[] Manfred Kraus (University of Tübingen)
-		\item[] Maarten van Leeuwen (Leiden University)
-		\item[] Christoph Lumer (University of Siena)
-		\item[] Fabrizio Macagno (Universidade NOVA de Lisboa)
-		\item[] Andrei Moldovan (University of Salamanca)
-		\item[] Paula Olmos (Universidad Autónoma de Madrid)
-		\item[] Rudi Palmieri (University of Liverpool)
-		\item[] Steven Patterson (Marygrove College)
-		\item[] Niki Pfeifer (Munich Center for Mathematical Philosophy)
-		\item[] Gilbert Plumer (Law School Admission Council) (retired)
-		\item[] Lotte van Poppel (University of Amsterdam)
-		\item[] Henry Prakken (University of Groningen)
-		\item[] Martin Reisigl (University of Bern)
-		\item[] Adam Richards (Texas Christian University)
-		\item[] Juho Ritola (University of Helsinki)
-		\item[] Andrea Rocci (Università della Svizzera Italiana)
-		\item[] Harvey Siegel (University of Miami)
-		\item[] Francisca Snoeck Henkemans (University of Amsterdam)
-		\item[] Manfred Stede (University of Potsdam)
-		\item[] Katharina Stevens (University of Lethbridge)
-		\item[] Christopher Tindale (University of Windsor)
-		\item[] Assimakis Tseronis (Örebro University)
-		\item[] Mariusz Urbanski (Adam Mickiewicz University)
-		\item[] Hans Vilhelm Hansen (University of Windsor)
-		\item[] Laura Vincze (Universityt of Pisa)
-		\item[] Jacky Visser (University of Dundee)
-		\item[] Lena Wahlberg (Lund University)
-		\item[] Harry Weger (University of Central Florida)
-		\item[] David Williams (Florida Atlantic University)
-		\item[] Harald Wohlrapp (Universität Hamburg)
-		\item[] Carly Woods (University of Maryland)
-		\item[] Yun Xie (Sun Yat-sen University)
-		\item[] Minghui Xiong (Sun Yat-sen University)
-		\item[] Igor Z. Zagar (Educational Research Institute)
-		\item[] Marta Zampa (Zurich University of Applied Sciences)
-		\item[] David Zarefsky (Northwestern University)
-		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
-	\end{compactitem}
-
-\newpage
-
 \section*{Keynote Speakers}

### 2020-05-10 prep.tex
Move keynote after preface

@@
 	\end{compactitem}
-
-\cleardoublepage
-
-\section*{Keynote Speakers}
-	\addcontentsline{toc}{chapter}{Keynote Speakers}
-\subsection*{Critical thinking as discourse}
-\emph{Deanna Kuhn} -- \emph{Columbia University}
-\\\\
-Less than it is an individual ability or skill, critical thinking is a dialogic practice people engage in and commit to, initially interactively and then in interiorized form with the other only implicit.
-An argument depends for its meaning on how others respond (Gergen, 2015).
-In advancing arguments, well-practiced thinkers anticipate their defeasibility as a consequence of others’ objections, in addition envisioning their own potential rebuttals.
-Whether in external or interiorized form, the dialogic process creates something new, while itself undergoing development.
-
-This perspective may be useful in sharpening definition of the construct of critical thinking and in so doing help to bring together the largely separate strands of work examining it as a theoretical construct, a measurable skill, and an educational objective.
-Implications for education follow.
-How might critical thinking as a shared practice be engaged in within educational settings in ways that will best support its development?
-One step is to privilege frequent practice of direct peer-to-peer discourse.
-A second is to take advantage of the leveraging power of dialog as a bridge to individual argument – one affording students’ argumentative writing a well-envisioned audience and purpose.
-Illustrations of this bridging power are presented.
-Finally, implications for assessment of critical thinking are noted and a case made for the value of people’s committing to a high standard of critical thinking as a shared and interactive practice.
-
-\subsection*{Revisiting Apologie de la polémique: about some “felicity conditions” allowing for coexistence in dissent}
-\emph{Ruth Amossy} -- \emph{Tel-Aviv University}
-\\\\
-In my book entitled Apologie de la polémique (2014), I claimed that polemical discourse fulfils various social functions, among which “coexistence in dissensus” seems the most important.
-It means not only that disagreement is the basis of life in society, and the principle on which argumentation as a common, rational search for the reasonable, is built.
-It also signifies that agreement cannot always be reached in democratic societies recognizing the importance of diversity and difference, so that disagreement has to be managed through verbal confrontations, namely, agonistic discussions and polemical exchanges.
-It thus appears that the latter, though generally blamed for its radicalization and polarization, plays an important role in the public sphere.
-Among others, public polemics helps opposite parties to voice conflicting opinions and fight for antagonistic solutions without recurring to arms.
-To use Chantal Mouffe’s words, it transforms “enemies” to be destroyed into “adversaries” who have a right to speak.
-Beside other social functions discussed in the book, polemics authorizes what the French call a “vivre-ensemble” – the possibility for people who do not share the same opinions, if not the same premises, to share the same national space and live together without outbursts of violence.
-
-However, the emphasis on dissent and its polemical management is not without raising multiple questions concerning the conditions of possibility and the limits of the so-called coexistence in dissent.
-Obviously, the use of polemical discourse is not enough to prevent citizens from physically fighting each other and even, sometimes, to dispel the specter of civil war.
-Outbursts of violence against refugees regularly occur in Germany where the polemical discussion is vivid.
-In France, the polemical exchanges on Emmanuel Macrons’ reforms and the authorized street demonstrations did not prevent urban violence.
-Even if polemical campaign discourse is tolerated, it did not prevent armed confrontations in certain African countries such as Ivory Coast.
-What, then, are the “felicity conditions” needed in order for public polemics to secure a peaceful “living together” in the framework of persistent and sometimes deep disagreements that can hardly be avoided in the democratic space?
-My contention is that to answer this question, it is necessary to explore polemical confrontations in their institutional framework, and to examine the functioning of polemical discourse in relation to the political, forensic and cultural factors that determine (at least partly) its degree of success.
-After synthetizing the finding of my first research into dissent and its polemical management, I will try – on the basis of a few case studies – to gather some of the “felicity conditions” necessary to make coexistence in dissent possible.
-
-\subsection*{Dissent needed: argumentation for AI and law applications}
-\emph{Katie Atkinson} -- \emph{University of Liverpool}
-\\\\
-As technological advances in artificial intelligence are being turned into deployed products, societal questions are being raised about the need for AI tools to be able to explain their decisions to humans.
-This need becomes even more pressing when AI technologies are applied in domains where critical decisions are made that can result in a significant effect upon individuals or groups in society.
-One such domain is law, where there is a thriving market developing in support tools for assisting with a variety of legal tasks carried out within law firms and the wider legal sector.
-Law is a domain rich in argumentation and support tools that are used to aid legal decision making should similarly be able to explain why a particular outcome of a decision has been reached, and not an alternative outcome.
-Dissent needs to be captured and revealed within AI reasoners to ensure that the decision space is explored from different perspectives, if AI tools are to be deployed effectively to assist with legal reasoning tasks.
-In this talk I will discuss a body of work on computational models of argument for legal reasoning and show how dissent features within this work to promote scrutability of AI decision making.

### 2020-05-12 papers-vol-2.tex
Split into three volumes

@@
 \insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
-\insertmydocument{chapter}{The Spaces and Places of Argumentation: Developing a Spatial Model of Argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
-\insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse
-(An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
-\insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
-\insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
-\addtocontents{toc}{\protect\newpage}
-\insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
-\insertmydocument{chapter}{A Decision Tree for Annotating Argumentation Scheme Corpora}{John Lawrence, Jacky Visser, Douglas Walton, Chris Reed}{pdfs/regular/71regularLawrence.doc.pdf} % 71
-\insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
-\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico E. L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
-\insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.
-Kline}{pdfs/regular/78regularManohar.doc.pdf} % 78
-\insertmydocument{chapter}{Holism of Reasons and its Consequences for Argumentation Theory}{Hubert Marraud}{pdfs/regular/80regularMarraud.doc.pdf} % 80
-\insertmydocument{chapter}{“Why did not your correspondent make an honest inquiry before so writing?”: The Text Structure and Discourse of Disagreement in Irish letters to the Editor}{Davide Mazzi}{pdfs/regular/81regularMazzi.doc.pdf} % 81
-\insertmydocument{chapter}{An Argumentative Approach to the Justification of Abduction}{Paula Olmos}{pdfs/regular/86regularOlmos.doc.pdf} % 86
-\insertmydocument{chapter}{When You Can’t Trust What You Don’t Know: Organ and Tissue Donation, Public Trust, the Voice of Dissent and Informed Consent}{Harmony Peach}{pdfs/regular/91regularPeach.doc.pdf} % 91
-\insertmydocument{chapter}{“The worst ever conceived by a man of genius.
-” Hume’s Probability Argument in A Treatise}{Jeanne Peijnenburg, David Atkinson}{pdfs/regular/92regularPeijnenburg.docx.pdf} % 92
-\insertmydocument{chapter}{Character, Dog Whistles, and the Limits of Charity}{Kathryn Phillips}{pdfs/regular/94regularPhillips.doc.pdf} % 94
-\insertmydocument{chapter}{The Rhetorical Potential of Metaphor: An Experimental Study on the Effect of Metaphors in Argumentation}{Roosmaryn Pilgram}{pdfs/regular/97regularPilgram.docx.pdf} % 97
-\insertmydocument{chapter}{Separate Opinions as an Argumentative Activity Type}{H. Jos\'{e} Plug}{pdfs/regular/98regularPlug.doc.pdf} % 98
-\insertmydocument{chapter}{Can Literary Fiction be Suppositional Reasoning?}{Gilbert Plumer}{pdfs/regular/99regularPlumer.doc.pdf} % 99
-\insertmydocument{chapter}{Conspiracy Theories and Reasonable Disagreement}{Juho Ritola}{pdfs/regular/106regularRitola.doc.pdf} % 106
-\insertmydocument{chapter}{Inference to the Best Metaphor}{Cristi\'{a}n Santib\'{a}\~{n}ez}{pdfs/regular/107regularSantibanez.docx.pdf} % 107
-\insertmydocument{chapter}{Beyond Randomized Clinical Trials: Emerging Innovations in Reasoning About Health}{Jodi Schneider, Sally Jackson}{pdfs/regular/109regularSchneider.docx.pdf} % 109
-\insertmydocument{chapter}{Multimodal Argumentation and Dissent -- a Perspective of Multimodal Critical Discourse Analysis}{Andrea Sabine Sedlaczek}{pdfs/regular/111regularSedlaczek.doc.pdf} % 111
-\insertmydocument{chapter}{Analogical Argumentation in Philosophical Thought Experiments}{Stefan Sleeuw}{pdfs/regular/112regularSleeuw.docx.pdf} % 112
-\insertmydocument{chapter}{Detecting and Handling Disagreement in Multi-party Health Coaching}{Mark Snaith, Alison Pease, Dominic De Franco}{pdfs/regular/113regularSnaith.doc.pdf} % 113
-\insertmydocument{chapter}{Explaining Away and the Propensity Interpretation of Probability: the Case of Unequal Priors}{Alice Liefgreen, Marko Te\v{s}i\'{c}}{pdfs/regular/116regularLiefgreen.docx.pdf} % 116
-\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/regular/118regularToniolo.doc.pdf} % 118
-\insertmydocument{chapter}{Disagreement in Aristotle’s Topics and its Latin Medieval Reception}{Gustavo Fern\'{a}ndez Walker, Ana Mar\'{i}a Mora-M\'{a}rquez}{pdfs/regular/122regularWalker.docx.pdf} % 122
-\insertmydocument{chapter}{Conductive Arguments. Towards a Solution of the Riddles}{Harald R. Wohlrapp}{pdfs/regular/125regularWohlrapp.doc.pdf} % 125
-\insertmydocument{chapter}{A Ludological Perspective on the Shape of Argument: Collaborative Assent to Dissenting Opposition}{Michael A. Yong-Set}{pdfs/regular/126regularYong-Set.docx.pdf} % 126
-\insertmydocument{chapter}{Towards the Justification of Warrant in a Legal Hard Case: How to Justify a Legal Rule by the Backing}{Shiyang Yu, Xi Chen}{pdfs/regular/127regularYu.docx.pdf} % 127
-\insertmydocument{chapter}{How Should We Classify Argument Schemes?}{David Zarefsky}{pdfs/regular/129regularZarefsky.doc.pdf} % 129

### 2020-05-12 papers-vol-3.tex
Split into three volumes

--- 2020-04-14 papers.tex
@@
-% TODO
-% [ ] move each commentary directly after each long paper
-% [ ] fill in titles of commentaries
-% [ ] fill in full author for each commentary
-% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)
-
-\part{Long papers}
-
-\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
-\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}
-
-\insertmydocument{chapter}{Is There an Informal Logic Approach to Argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
-\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}
-
-\insertmydocument{chapter}{Structural Differences Between Practical and Cognitive Presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
-\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural Differences Between Practical and Cognitive Presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}
-
-\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/6longCacean.docx.pdf}
-\insertmydocument{chapter}{Commentary on Cacean’s Reliability of Argument Mapping}{Roosmaryn Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
-
-\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
-\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}
-
-\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/8longCorredor.docx.pdf}
-\insertmydocument{chapter}{Dissent and Democracy -- Commentary on Corredor’s Democratic Legitimacy and Acts of Dissent}{David Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}
-
-\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
-\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}
-
-\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
-\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}
-
-\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
-\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}
-
-\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/12longHannkenilljes.docx.pdf}
-
-\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
-\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}
-
-\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/14longHoffmann.doc.pdf}
-
-\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
-\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}
-
-\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
-\insertmydocument{chapter}{A wanting analysis -- Commentary on S.
-Jackson, S.
-Jacobs, Y.
-Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R.
-Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}
-
-\insertmydocument{chapter}{Speech Act Pluralism in Argumentative Polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}
-
-\insertmydocument{chapter}{Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
-\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}
-
-\insertmydocument{chapter}{Arguments From Expert Opinion – An Epistemological Approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}
-
-\insertmydocument{chapter}{All-out Attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}
-
-\insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H.
-Reijven}{pdfs/long/22longReijven.doc.pdf}
-\insertmydocument{chapter}{Commentary on Reijven’s Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Beth Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}
-
-\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
-\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}
-
-\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/24longSinclair.doc.pdf}
-\insertmydocument{chapter}{Commentary on Sinclair’s Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate about Funding Prep}{Sally Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}
-
-\insertmydocument{chapter}{Strange Fish: Belief and the Roots of Disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
-\insertmydocument{chapter}{An optimistic perspective on deep disagreement?
-Commentary on Tindale’s Strange Fish: Belief and the Roots of Disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}
-
-\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
-\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}
-
-% \addtocontents{toc}{\protect\newpage}
 \part{Regular papers}
 
-\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
-\insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
-\insertmydocument{chapter}{Epistemic Tolerance}{Dominik Balg}{pdfs/regular/7regularBalg.doc.pdf} % 7
-\insertmydocument{chapter}{Structuring Controversy: The Dialectic of Disagreement}{Sharon Bailin, Mark Battersby}{pdfs/regular/8regularBailin.docx.pdf} % 8
-\insertmydocument{chapter}{The Role of Reasoning and Arguing in Youth Democratic Participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
-\insertmydocument{chapter}{Pictures and Reasoning: Visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
-\insertmydocument{chapter}{Issues Leading to Argumentative Discussions During Family Mealtime Conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
-\insertmydocument{chapter}{Value-based Argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
-\insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
-\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
-\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
-\insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
-Cheng}{pdfs/regular/20regularCheng.docx.pdf} % 20
-\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
-\insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
-\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
-\insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
-\insertmydocument{chapter}{Arguing Brexit on Twitter: A Corpus Linguistic Study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
-\insertmydocument{chapter}{Protagoras’ Principles, Disagreement and the Possibility of Error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
-\insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
-\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
-\insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
-\insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
-\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
-\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
-\insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
-\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
-\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.doc.pdf} % 47
-\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
-\insertmydocument{chapter}{Towards a Theory of Informal Argument Semantics}{Martin Hinton}{pdfs/regular/49regularHinton.doc.pdf} % 49
-\insertmydocument{chapter}{Stereotyping}{David Hitchcock}{pdfs/regular/50regularHitchcock.doc.pdf} % 50
-\insertmydocument{chapter}{Changing Norms of Argumentation}{Beth Innocenti}{pdfs/regular/53regularInnocenti.doc.pdf} % 53
-\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
-\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.doc.pdf} % 55
-\insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57
 \insertmydocument{chapter}{The Spaces and Places of Argumentation: Developing a Spatial Model of Argumentation}{Steven Johnson}{pdfs/regular/58regularJohnson.docx.pdf} % 58
 \insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
+\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse
+(An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
 \insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
 \insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
+\addtocontents{toc}{\protect\newpage}
 \insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70
@@
 \insertmydocument{chapter}{Philosophical Foundation of Reasonableness in Mencius’s Argumentative Discourse: Based on the use of dissociation}{Yan Linqiong, Xiong Minghui}{pdfs/regular/72regularYanXiong.docx.pdf} % 72
-\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
-\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
+\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
+\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico E. L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75
 \insertmydocument{chapter}{Dissent as a Voice of Support: The Influence of Argument Types in Providing Support to Those Who have Experienced Racial Discrimination}{Uttara Manohar, Susan L.

### 2020-05-12 preface.tex
Split into three volumes

@@
 After two successful editions held in Lisbon in 2015 and Fribourg in 2017, ECA was hosted in 2019 by the Faculty of Philosophy of the University of Groningen, on 24-27 June 2019.
-These two volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.
+These three volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.
 
@@
 How has dissent been conceptualized in the history of rhetoric, dialectic and logic?
-The papers in these two volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).
+The papers in these three volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).
 
@@
 These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation.
-The contents of these two volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
+The contents of these three volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
 
@@
 In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants.
-Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these two volumes, and assisted us throughout in the process of producing the Proceedings.
+Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these three volumes, and assisted us throughout in the process of producing the Proceedings.
 

### 2020-05-13 papers-vol-1.tex
Fix margins on first few pages

@@
 \insertmydocument{chapter}{Commentary on Cacean’s Reliability of Argument Mapping}{Roosmaryn Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}
+
+\addtocontents{toc}{\protect\newpage}
 
@@
 \insertmydocument{chapter}{Visual Argument Schemes in the PTA}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
-\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry
-}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
+\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
 \insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
@@
 \insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, Kamila Debowska-Kozlowska, David Godden, Marcin Selinger, Simon Wells}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
+
+\addtocontents{toc}{\protect\newpage}
+
 \insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}

### 2020-05-13 papers-vol-3.tex
Fix margins on first few pages

@@
 \insertmydocument{chapter}{Aggressiveness as a Qualifier of Dissent in Interpersonal Arguing}{Iryna Khomenko}{pdfs/regular/59regularKhomenko.docx.pdf} % 59
-\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse
-(An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
+\insertmydocument{chapter}{Auditory Arguments – Importance of Sound in an Argumentative Discourse (An Empirical Study)}{Gabrijela Ki\v{s}i\v{c}ek}{pdfs/regular/60regularKisicek.docx.pdf} % 60
 \insertmydocument{chapter}{Be reasonable! Ways to React to Cases of Presumed Unreason}{Erik C. W. Krabbe, Jan Albert van Laar}{pdfs/regular/65regularKrabbe.doc.pdf} % 65
 \insertmydocument{chapter}{Epistemic Injustice and Deep Disagreement}{Thirza Lagewaard}{pdfs/regular/69regularLagewaard.doc.pdf} % 69
-\addtocontents{toc}{\protect\newpage}
 \insertmydocument{chapter}{Argumentative Patterns of Right-Wing Populism: The Example of the “Alternative for Germany”}{David Lanius}{pdfs/regular/70regularLanius.doc.pdf} % 70

### 2020-05-14 authors.py
Fix author index page error edge case (Thanks David!)

@@ -42,14 +42,15 @@ if __name__ == '__main__':
 			line = line.rstrip()
 			match = pattern.match(line)
 			if match:
+				print('\\insertmydocument{{chapter}}{{{title}}}{{{authors}}}{{{file}}}{{%'.format(**match.groupdict()))
 				for author in parse_authors(match.group('authors')):
-					print(r'\index[authors]{{{1}@{0}}}'.format(', '.join(author), sortable_str(', '.join(author))))
-				print(r'\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}'.format(
+					print(r'\index[authors]{{{1}@{0}}}%'.format(', '.join(author), sortable_str(', '.join(author))))
+				print('\\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}%'.format(
 					section=match.group('title'),
 					id=parse_filename(match.group('file'))))
-			print(line)
-			if match:
-				print("")
+				print('}}{comment}'.format(**match.groupdict()))
+			else:
+				print(line)
 		print(r"Done! Don't forget to enable imakeidx:\n  \usepackage{imakeidx}\n  \makeindex[name=authors,title=Index of Authors,options=-r]", file=sys.stderr)
 	except ValueError as e:
 		print(e, file=sys.stderr)

### 2020-05-21 papers-vol-2.tex
Fix margins on first few pages
Don't add the "Part I" in volumes II and III
Fix author's position in author index
Fix compilation error

@@
-\part{Regular papers}
+\addcontentsline{toc}{part}{Regular papers}
+\part*{Regular papers}
 
@@
 \insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel H. Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
-\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
+\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra~Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
 \insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S.
@@
 \insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation (AdArg)}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
-\addtocontents{toc}{\protect\newpage}
 \insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
@@
 \insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.docx.pdf} % 47
-\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
+\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of `Everyone knows X'}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
 \insertmydocument{chapter}{Towards a Theory of Informal Argument Semantics}{Martin Hinton}{pdfs/regular/49regularHinton.doc.pdf} % 49
@@
 \insertmydocument{chapter}{Changing Norms of Argumentation}{Beth Innocenti}{pdfs/regular/53regularInnocenti.doc.pdf} % 53
-\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
+\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.docx.pdf} % 54
 \insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.docx.pdf} % 55

### 2020-05-21 authors.py
Don't print "none" if there is no latex comment in the papers-vol-*.tex file

@@ -48,7 +48,7 @@ if __name__ == '__main__':
 				print('\\pdfbookmark[chapter]{{{section}}}{{paper-{id}}}%'.format(
 					section=match.group('title'),
 					id=parse_filename(match.group('file'))))
-				print('}}{comment}'.format(**match.groupdict()))
+				print('}}{comment}'.format(comment=match.group('comment') or ''))
 			else:
 				print(line)
 		print(r"Done! Don't forget to enable imakeidx:\n  \usepackage{imakeidx}\n  \makeindex[name=authors,title=Index of Authors,options=-r]", file=sys.stderr)

### 2020-05-21 prep.tex
Incorporate minor changes requested
Fix Goddu in preface
Fix affiliations in steering committee
Last minute affiliation changes

@@
 		\item[] Catarina Dutilh Novaes (Vrije Universiteit Amsterdam)
-		\item[] Henrike Jansen (University of Leiden)
+		\item[] Henrike Jansen (Leiden University)
 		\item[] Jan Albert Van Laar (chair) (University of Groningen)
@@
 		\item[] Dale Hample (chair) (University of Maryland)
-		\item[] Henrike Jansen (secretary) (University of Leiden)
+		\item[] Henrike Jansen (secretary) (Leiden University)
 		\item[] Marcin Lewinski (Universidade Nova de Lisboa)
@@
 		\item[] Lilian Bermejo Luque (University of Granada)
-		\item[] Katarzyna Budzyńska (Polish Academy of Sciences)
-		\item[] Henrike Jansen (University of Leiden)
-		\item[] Marcin Koszowy (University of Białystok)
+		\item[] Katarzyna Budzyńska (Warsaw University of Technology)
+		\item[] Henrike Jansen (Leiden University)
+		\item[] Marcin Koszowy (Warsaw University of Technology)
 		\item[] Jan Albert Van Laar (deputy chair) (University of Groningen)
@@
 		\item[] David Godden (Michigan State University)
-		\item[] C. Goddu (University of Richmond)
+		\item[] G.C. Goddu (University of Richmond)
 		\item[] Jean Goodwin (North Carolina State University)
@@
 		\item[] Jérôme Jacquin (University of Lausanne)
-		\item[] Henrike Jansen (University of Leiden)
+		\item[] Henrike Jansen (Leiden University)
 		\item[] Amy Johnson (University of Oklahoma)
@@
 		\item[] Hans Vilhelm Hansen (University of Windsor)
-		\item[] Laura Vincze (Universityt of Pisa)
+		\item[] Laura Vincze (University of Pisa)
 		\item[] Jacky Visser (University of Dundee)
@@
 		\item[] David Zarefsky (Northwestern University)
-		\item[] Gabor Zemplen (Budapest University of Technology and Economics)
+		\item[] Gábor Zemplén (Eötvös Loránd University)
 	\end{compactitem}

### 2020-05-21 preface.tex
Mention the three volumes in preface
gathers -> gather
Fix paper count in preface
Oops :(
Add grant to preface

@@
 Volume I gathers 25 long papers and associated commentaries, together with 9 papers presented in the thematic panels that were held during ECA2019.
-Volume II gathers 67 regular papers that were presented during the conference.
+Volumes II and III gather 69 regular papers that were presented during the conference.
 
@@
 Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these three volumes, and assisted us throughout in the process of producing the Proceedings.
+Thanks also to the European Research Council for generously supporting the production of the Proceedings by means of grant ERC-17-CoG 771074 for the project `The Social Epistemology of Argumentation' (PI C.
+Dutilh Novaes).
 

### 2020-05-21 preface.tex
Shorten preface to fit on one page

@@
 
-The conference had 224 participants, and 188 papers were presented.
-These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation.
-The contents of these three volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.
+ECA 2019 had 224 participants and 188 paper presentations, a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field.
+These three volumes reflect the current state of the art in argumentation scholarship in general.
 
